### 2024-11-23 paper/paper.qmd
drew graphs

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(arrow)
library(MASS)
library(GGally)
library(gridExtra)

data <- read_parquet(here::here("data/02-analysis_data/bodyfat.parquet"))
```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| echo: false
#| warning: false
#| message: false

# Histogram for Pct.BF
hist(data$Pct.BF, 
     main = "Histogram of Percent Body Fat",
     xlab = "Percent Body Fat",
     col = "lightblue",
     border = "black",
     breaks = 20)
```

Talk more about it.

## Predictor variables

variables of interest: Age Height Abdomen Wrist

Reference appendix for how variables were picked using backward selection method

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

```{r}
#| echo: false
#| warning: false
#| message: false

# Create a layout for multiple plots
par(mfrow = c(2, 2), mar = c(4, 4, 2, 1))  # 2 rows and 4 columns

# Histogram for each variable
hist(data$Age, main = "Histogram of Age", xlab = "Age", col = "#7dbeff", border = "black")
hist(data$Height, main = "Histogram of Height", xlab = "Height (inches)", col = "#2aebaa", border = "black")
hist(data$Abdomen, main = "Histogram of Abdomen", xlab = "Abdomen (cm)", col = "#eb49a4", border = "black")
hist(data$Wrist, main = "Histogram of Wrist", xlab = "Wrist (cm)", col = "#bb86f7", border = "black")
```

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

$y_i = \beta_0 + \beta_1 x_{1i} + \beta_2 x_{2i} + \beta_3 x_{3i} + \beta_4 x_{4i}$

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

Linear reg assumptions
```{r}
#| echo: false
#| warning: false
#| message: false

# Fit the linear regression model
model <- lm(Pct.BF ~ Age + Height + Abdomen + Wrist, data = data)

# 1. Linearity: Residuals vs Fitted Plot
plot(model$fitted.values, residuals(model), 
     main = "Residuals vs Fitted",
     xlab = "Fitted Values",
     ylab = "Residuals")
abline(h = 0, col = "red")
```

```{r}
#| echo: false
#| warning: false
#| message: false

# 2. Independence: Durbin-Watson Test (requires car package)
# install.packages("car")  # Uncomment to install if not already installed
library(car)
durbinWatsonTest(model)
```

```{r}
#| echo: false
#| warning: false
#| message: false

# 3. Homoscedasticity: Scale-Location Plot
plot(model, which = 3)
```

```{r}
#| echo: false
#| warning: false
#| message: false

# 4. Normality: Q-Q Plot of Residuals
qqnorm(residuals(model))
qqline(residuals(model), col = "red")
```

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| warning: false
#| message: false

p1 <- ggplot(data, aes(x = Age, y = Pct.BF)) +
  geom_point(color = "#7dbeff", alpha = 0.5) +
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  labs(title = "Pct.BF vs Age", x = "Age", y = "Pct.BF") +
  theme_minimal()

p2 <- ggplot(data, aes(x = Height, y = Pct.BF)) +
  geom_point(color = "#2aebaa", alpha = 0.5) +
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  labs(title = "Pct.BF vs Height", x = "Height (inches)", y = "Pct.BF") +
  theme_minimal()

p3 <- ggplot(data, aes(x = Abdomen, y = Pct.BF)) +
  geom_point(color = "#eb49a4", alpha = 0.5) +
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  labs(title = "Pct.BF vs Abdomen", x = "Abdomen (cm)", y = "Pct.BF") +
  theme_minimal()

p4 <- ggplot(data, aes(x = Wrist, y = Pct.BF)) +
  geom_point(color = "#bb86f7", alpha = 0.5) +
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  labs(title = "Pct.BF vs Wrist", x = "Wrist (cm)", y = "Pct.BF") +
  theme_minimal()

grid.arrange(p1, p2, p3, p4, nrow = 2, ncol = 2)
```

```{r}
#| echo: false
#| warning: false
#| message: false

model <- lm(Pct.BF ~ Age + Height + Abdomen + Wrist, data = data)
summary(model)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

```{r}
#| echo: false
#| warning: false
#| message: false

data <- data[ , !(names(data) %in% c("Density"))]

# Full model using all variables except Density
full_model <- lm(Pct.BF ~ ., data = data)

# Perform backward selection
backward_model <- stepAIC(full_model, direction = "backward", trace = 0)

# Extract the final 4-variable model
final_variables <- names(coef(backward_model))[-1] # Exclude intercept
while (length(final_variables) > 4) {
  current_model <- lm(as.formula(paste("Pct.BF ~", paste(final_variables, collapse = "+"))), data = data)
  current_aic <- AIC(current_model)

  # Drop one variable at a time and calculate AIC
  aic_values <- sapply(final_variables, function(var) {
    temp_model <- lm(as.formula(paste("Pct.BF ~", paste(setdiff(final_variables, var), collapse = "+"))), data = data)
    return(AIC(temp_model))
  })

  # Remove the variable leading to the lowest AIC improvement
  final_variables <- setdiff(final_variables, names(which.min(aic_values)))
}

# Final 4-variable model
final_model <- lm(as.formula(paste("Pct.BF ~", paste(final_variables, collapse = "+"))), data = data)

# Print the AIC value and final variables
cat("AIC:", AIC(final_model), "\n")
cat("Variables:", final_variables, "\n")
```

Multicollinear between picked vars 
```{r}
#| echo: false
#| warning: false
#| message: false

# Select the specified variables
selected_data <- data[, c("Age", "Height", "Abdomen", "Wrist")]

# Generate a pairwise plot
pairwise_plot <- ggpairs(selected_data, 
                         lower = list(continuous = wrap("points", color = "#008080", alpha = 0.4)), 
                         upper = list(continuous = wrap("points", color = "#008080", alpha = 0.4)),
                         diag = list(continuous = wrap("densityDiag", fill = "#008080", alpha = 0.6)))

# Print the plot
print(pairwise_plot)
```

\newpage

# References

### 2024-11-23 scripts/02-clean_data.R

@@ -1,47 +1,0 @@
-#### Preamble ####
-# Purpose: Downloads and saves the data from DASL
-# Author: Wendy Yuan
-# Date: 29 November 2024
-# Contact: w.yuan@mail.utoronto.ca 
-
-#### Workspace setup ####
-library(tidyverse)
-library(arrow)
-library(readr)
-library(dplyr)
-library(tidyr)
-
-#### Clean data ####
-data <- read.table("data/01-raw_data/bodyfat.txt", header = TRUE, sep = "\t")
-
-# Select relevant columns
-selected_data <- data %>%
-  select(Pct.BF, Neck, Chest, Abdomen, Wrist, Weight)
-
-# Handle missing values
-cleaned_data <- selected_data %>%
-  drop_na()
-
-# Remove duplicates
-cleaned_data <- cleaned_data %>%
-  distinct()
-
-# Function to remove outliers
-remove_outliers <- function(data, column) {
-  Q1 <- quantile(data[[column]], 0.25, na.rm = TRUE)
-  Q3 <- quantile(data[[column]], 0.75, na.rm = TRUE)
-  IQR <- Q3 - Q1
-  lower_bound <- Q1 - 1.5 * IQR
-  upper_bound <- Q3 + 1.5 * IQR
-  data %>%
-    filter(data[[column]] >= lower_bound & data[[column]] <= upper_bound)
-}
-
-# Apply outlier removal to each column
-columns_to_check <- c("Pct.BF", "Neck", "Chest", "Abdomen", "Wrist")
-for (col in columns_to_check) {
-  cleaned_data <- remove_outliers(cleaned_data, col)
-}
-
-#### Save data ####
-write_parquet(cleaned_data, "data/02-analysis_data/bodyfat.parquet")

### 2024-11-23 scripts/02-download_data.R

@@ -1,0 +1,16 @@
+#### Preamble ####
+# Purpose: Downloads and saves the data from DASL
+# Author: Wendy Yuan
+# Date: 29 November 2024
+# Contact: w.yuan@mail.utoronto.ca 
+
+#### Workspace setup ####
+library(opendatatoronto)
+library(tidyverse)
+
+#### Download data ####
+
+
+
+#### Save data ####
+write_csv(the_raw_data, "inputs/data/raw_data.csv")

### 2024-11-23 scripts/03-clean_data.R

@@ -1,0 +1,26 @@
+#### Preamble ####
+# Purpose: Downloads and saves the data from DASL
+# Author: Wendy Yuan
+# Date: 29 November 2024
+# Contact: w.yuan@mail.utoronto.ca 
+
+#### Workspace setup ####
+library(tidyverse)
+library(arrow)
+library(readr)
+library(dplyr)
+library(tidyr)
+
+#### Clean data ####
+data <- read.table("data/01-raw_data/bodyfat.txt", header = TRUE, sep = "\t")
+
+# Handle missing values
+cleaned_data <- data %>%
+  drop_na()
+
+# Remove duplicates
+cleaned_data <- cleaned_data %>%
+  distinct()
+
+#### Save data ####
+write_parquet(cleaned_data, "data/02-analysis_data/bodyfat.parquet")

### 2024-11-23 scripts/03-test_analysis_data.R

@@ -1,69 +1,0 @@
-#### Preamble ####
-# Purpose: Tests cleaned data
-# Author: Wendy Yuan
-# Date: 29 November 2024
-# Contact: w.yuan@mail.utoronto.ca
-# Pre-requisites: 
-# - 02-clean_data.R must have been run
-
-#### Workspace setup ####
-library(tidyverse)
-library(testthat)
-library(dplyr)
-
-# Load the cleaned dataset
-cleaned_data <- read_parquet("data/02-analysis_data/bodyfat.parquet")
-
-#### Test cleaned data ####
-
-# Test that the dataset has rows - there should be some rows after cleaning
-test_that("dataset has rows", {
-  expect_gt(nrow(cleaned_data), 0)  # Ensure at least 1 row exists
-})
-
-# Test that the dataset has 6 columns
-test_that("dataset has 6 columns", {
-  expect_equal(ncol(cleaned_data), 6)
-})
-
-# Test that all selected columns exist
-test_that("required columns exist", {
-  expect_true(all(c("Pct.BF", "Neck", "Chest", "Abdomen", "Wrist", "Weight")
-                  %in% colnames(cleaned_data)))
-})
-
-# Test that all columns are numeric
-test_that("all columns are numeric", {
-  expect_true(all(sapply(cleaned_data, is.numeric)))
-})
-
-# Test that individual columns are numeric (optional redundancy)
-columns_to_check <- c("Pct.BF", "Neck", "Chest", "Abdomen", "Wrist")
-for (col in columns_to_check) {
-  test_that(paste0(col, " is numeric"), {
-    expect_type(cleaned_data[[col]], "double")  # "double" for numeric values
-  })
-}
-
-# Test that there are no missing values in the dataset
-test_that("no missing values in dataset", {
-  expect_true(all(!is.na(cleaned_data)))
-})
-
-# Test that there are no duplicate rows
-test_that("no duplicate rows in dataset", {
-  expect_equal(nrow(cleaned_data), nrow(distinct(cleaned_data)))
-})
-
-# Test that outliers were removed based on IQR (values within bounds)
-for (col in columns_to_check) {
-  test_that(paste0(col, " does not contain outliers"), {
-    Q1 <- quantile(cleaned_data[[col]], 0.25, na.rm = TRUE)
-    Q3 <- quantile(cleaned_data[[col]], 0.75, na.rm = TRUE)
[…]

### 2024-11-23 scripts/04-test_analysis_data.R

@@ -1,0 +1,43 @@
+#### Preamble ####
+# Purpose: Tests cleaned data
+# Author: Wendy Yuan
+# Date: 29 November 2024
+# Contact: w.yuan@mail.utoronto.ca
+# Pre-requisites: 
+# - 02-clean_data.R must have been run
+
+#### Workspace setup ####
+library(tidyverse)
+library(testthat)
+library(arrow)
+library(dplyr)
+
+# Load the cleaned dataset
+cleaned_data <- read_parquet("data/02-analysis_data/bodyfat.parquet")
+
+#### Test cleaned data ####
+
+# Test that the dataset has rows - there should be some rows after cleaning
+test_that("dataset has rows", {
+  expect_gt(nrow(cleaned_data), 0)  # Ensure at least 1 row exists
+})
+
+# Test that all columns in the dataset exist
+test_that("all columns exist", {
+  expect_true(all(colnames(cleaned_data) %in% colnames(cleaned_data)))
+})
+
+# Test that all columns are numeric
+test_that("all columns are numeric", {
+  expect_true(all(sapply(cleaned_data, is.numeric)))
+})
+
+# Test that there are no missing values in the dataset
+test_that("no missing values in dataset", {
+  expect_true(all(!is.na(cleaned_data)))
+})
+
+# Test that there are no duplicate rows
+test_that("no duplicate rows in dataset", {
+  expect_equal(nrow(cleaned_data), nrow(distinct(cleaned_data)))
+})

### 2024-11-23 paper/paper.qmd
updated some script files

@@
 author: 
-  - First author
-  - Another author
-thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
-date: today
+  - Wendy Yuan
+thanks: "Code and data are available at: https://github.com/kiwindyy/Body-Fat"
+date: November 29, 2024
 date-format: long
@@
 hist(data$Wrist, main = "Histogram of Wrist", xlab = "Wrist (cm)", col = "#bb86f7", border = "black")
+```
+
+Multicollinear between picked vars 
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+
+# Select the specified variables
+selected_data <- data[, c("Age", "Height", "Abdomen", "Wrist")]
+
+# Generate a pairwise plot
+pairwise_plot <- ggpairs(selected_data, 
+                         lower = list(continuous = wrap("points", color = "#008080", alpha = 0.4)), 
+                         upper = list(continuous = wrap("points", color = "#008080", alpha = 0.4)),
+                         diag = list(continuous = wrap("densityDiag", fill = "#008080", alpha = 0.6)))
+
+# Print the plot
+print(pairwise_plot)
 ```
@@
 
-Multicollinear between picked vars 
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-
-# Select the specified variables
-selected_data <- data[, c("Age", "Height", "Abdomen", "Wrist")]
-
-# Generate a pairwise plot
-pairwise_plot <- ggpairs(selected_data, 
-                         lower = list(continuous = wrap("points", color = "#008080", alpha = 0.4)), 
-                         upper = list(continuous = wrap("points", color = "#008080", alpha = 0.4)),
-                         diag = list(continuous = wrap("densityDiag", fill = "#008080", alpha = 0.6)))
-
-# Print the plot
-print(pairwise_plot)
-```
-
 \newpage

### 2024-11-23 scripts/02-download_data.R

@@ -5,12 +5,16 @@
 # Contact: w.yuan@mail.utoronto.ca 
 
 #### Workspace setup ####
-library(opendatatoronto)
 library(tidyverse)
+library(dplyr)
+library(readr)
+
+# Dataset page : https://dasl.datadescription.com/datafile/bodyfat/
+url <- "https://dasl.datadescription.com/download/data/3079"
+saved_file <- "data/01-raw_data/bodyfat.txt"
 
 #### Download data ####
-
-
+text_content <- readLines(url)
 
 #### Save data ####
-write_csv(the_raw_data, "inputs/data/raw_data.csv")
+writeLines(text_content, saved_file)

### 2024-11-23 scripts/03-clean_data.R

@@ -15,12 +15,32 @@ library(tidyr)
 data <- read.table("data/01-raw_data/bodyfat.txt", header = TRUE, sep = "\t")
 
 # Handle missing values
-cleaned_data <- data %>%
-  drop_na()
+cleaned_data <- data %>% drop_na()
 
 # Remove duplicates
-cleaned_data <- cleaned_data %>%
-  distinct()
+cleaned_data <- cleaned_data %>% distinct()
+
+# define percentile curoff
+lower_cutoff = 0.25
+upper_cutoff = 0.75
+
+# Function to remove outlines
+remove_outliers <- function(data, column) {
+  Q1 <- quantile(data[[column]], lower_cutoff, na.rm = TRUE)
+  Q3 <- quantile(data[[column]], upper_cutoff, na.rm = TRUE)
+  IQR <- Q3 - Q1
+  lower_bound <- Q1 - 1.5 * IQR
+  upper_bound <- Q3 + 1.5 * IQR
+  data %>%
+    filter(data[[column]] >= lower_bound & data[[column]] <= upper_bound)
+}
+
+#Remove outliners by checking all columns
+for (column_name in colnames(cleaned_data)) {
+  if (is.numeric(cleaned_data[[column_name]])) {
+    cleaned_data <- remove_outliers(cleaned_data, column_name)
+  }
+}
 
 #### Save data ####
 write_parquet(cleaned_data, "data/02-analysis_data/bodyfat.parquet")

### 2024-11-24 paper/paper.qmd
fix some scripts & drew some more models

@@
 library(gridExtra)
+library(knitr)
+library(car)
+library(kableExtra)
 
 data <- read_parquet(here::here("data/02-analysis_data/bodyfat.parquet"))
+raw_data <- read.table(here::here("data/01-raw_data/bodyfat.txt"))
 ```
@@
 
+Why it matters paragraph
+
 Overview paragraph
-
-Estimand paragraph
 
@@
 
-Why it matters paragraph
+Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
 
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+## Estimand
+
+Estimand paragraph
 
@@
 Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+
+cleaned data with normalized measurement 
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+
+# Split into two smaller tables
+part1 <- data[, 1:8]  # First 8 columns
+part2 <- data[, 9:16]  # Remaining 8 columns
+
+# Render each part
+kable(head(part1, 10), booktabs = TRUE, caption = "Part 1: Columns 1-8") %>%
+  kable_styling(latex_options = c("hold_position", "scale_down"))
+
+kable(head(part2, 10), booktabs = TRUE, caption = "Part 2: Columns 9-16") %>%
+  kable_styling(latex_options = c("hold_position", "scale_down"))
+```
 
@@
      xlab = "Percent Body Fat",
-     col = "lightblue",
+     col = "#f88379",
      border = "black",
@@
 
+data <- data[ , !(names(data) %in% c("Density"))]
+
+# Full model using all variables except Density
+full_model <- lm(Pct.BF ~ ., data = data)
+
+# Perform backward selection
+backward_model <- stepAIC(full_model, direction = "backward", trace = 0)
+
+# Extract the final 4-variable model
+final_variables <- names(coef(backward_model))[-1] # Exclude intercept
+while (length(final_variables) > 4) {
+  current_model <- lm(as.formula(paste("Pct.BF ~", paste(final_variables, collapse = "+"))), data = data)
+  current_aic <- AIC(current_model)
+
+  # Drop one variable at a time and calculate AIC
+  aic_values <- sapply(final_variables, function(var) {
+    temp_model <- lm(as.formula(paste("Pct.BF ~", paste(setdiff(final_variables, var), collapse = "+"))), data = data)
+    return(AIC(temp_model))
+  })
+
+  # Remove the variable leading to the lowest AIC improvement
+  final_variables <- setdiff(final_variables, names(which.min(aic_values)))
+}
+
+# Final 4-variable model
+final_model <- lm(as.formula(paste("Pct.BF ~", paste(final_variables, collapse = "+"))), data = data)
+
+# Print the AIC value and final variables
+cat("AIC:", AIC(final_model), "\n")
+cat("Variables:", final_variables, "\n")
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+
 # Create a layout for multiple plots
@@
 
-Multicollinear between picked vars 
 ```{r}
@@
 
-# Select the specified variables
-selected_data <- data[, c("Age", "Height", "Abdomen", "Wrist")]
+model <- lm(Pct.BF ~ Age + Height + Abdomen + Wrist, data = data)
 
-# Generate a pairwise plot
-pairwise_plot <- ggpairs(selected_data, 
-                         lower = list(continuous = wrap("points", color = "#008080", alpha = 0.4)), 
-                         upper = list(continuous = wrap("points", color = "#008080", alpha = 0.4)),
-                         diag = list(continuous = wrap("densityDiag", fill = "#008080", alpha = 0.6)))
+# Calculate VIF
+vif_values <- vif(model)
 
-# Print the plot
-print(pairwise_plot)
+# Print VIF values
+print(vif_values)
 ```
@@
 
+Multicollinear between picked vars 
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+
+# Select the specified variables
+selected_data <- data[, c("Age", "Height", "Abdomen", "Wrist")]
+
+# Generate a pairwise plot
+pairwise_plot <- ggpairs(selected_data, 
+                         lower = list(continuous = wrap("points", color = "#008080", alpha = 0.4)), 
+                         upper = list(continuous = wrap("points", color = "#008080", alpha = 0.4)),
+                         diag = list(continuous = wrap("densityDiag", fill = "#008080", alpha = 0.6)))
+
+# Print the plot
+print(pairwise_plot)
+```
+
 ```{r}
@@
 
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+
+# Fit the model
+model <- lm(Pct.BF ~ Age + Height + Abdomen + Wrist, data = data)
+
+# Extract coefficients, standard errors, and calculate 90% confidence intervals
+coef_summary <- summary(model)$coefficients
+conf_intervals <- confint(model, level = 0.90)  # 90% confidence intervals
+
+# Create a data frame for plotting
+coeff_data <- data.frame(
+  Parameter = rownames(coef_summary),
+  Estimate = coef_summary[, "Estimate"],
+  Lower = conf_intervals[, 1],
+  Upper = conf_intervals[, 2]
+)
+
+# Remove the intercept for better visualization (optional)
+coeff_data <- coeff_data[coeff_data$Parameter != "(Intercept)", ]
+
+# Create the plot
+ggplot(coeff_data, aes(x = Estimate, y = Parameter)) +
+  geom_point(size = 3, color = "#f88379") +
+  geom_errorbarh(aes(xmin = Lower, xmax = Upper), height = 0.2,
+                 color = "#f88379", linewidth = 0.8) +
+  theme_minimal() +
+  labs(
+    title = "Model Coefficients",
+    subtitle = "90% Confidence Intervals",
+    x = "Coefficient Estimate",
+    y = "Predictors"
+  ) +
+  theme(
+    axis.title.y = element_text(size = 12, face = "bold"),
+    axis.text.y = element_text(size = 10),
+    plot.title = element_text(size = 14, face = "bold")
+  )
+
+```
+
 # Discussion
@@
 
+# Conclusion
+
 \newpage
@@
 
-data <- data[ , !(names(data) %in% c("Density"))]
+# Split into two smaller tables
+part1 <- raw_data[, 1:8]  # First 8 columns
+part2 <- raw_data[, 9:16]  # Remaining 8 columns
 
-# Full model using all variables except Density
-full_model <- lm(Pct.BF ~ ., data = data)
+# Render each part
+kable(head(part1, 10), booktabs = TRUE, caption = "Part 1: Columns 1-8") %>%
+  kable_styling(latex_options = c("hold_position", "scale_down"))
 
-# Perform backward selection
-backward_model <- stepAIC(full_model, direction = "backward", trace = 0)
-
-# Extract the final 4-variable model
-final_variables <- names(coef(backward_model))[-1] # Exclude intercept
-while (length(final_variables) > 4) {
-  current_model <- lm(as.formula(paste("Pct.BF ~", paste(final_variables, collapse = "+"))), data = data)
-  current_aic <- AIC(current_model)
-
-  # Drop one variable at a time and calculate AIC
-  aic_values <- sapply(final_variables, function(var) {
-    temp_model <- lm(as.formula(paste("Pct.BF ~", paste(setdiff(final_variables, var), collapse = "+"))), data = data)
-    return(AIC(temp_model))
-  })
-
-  # Remove the variable leading to the lowest AIC improvement
-  final_variables <- setdiff(final_variables, names(which.min(aic_values)))
-}
-
-# Final 4-variable model
-final_model <- lm(as.formula(paste("Pct.BF ~", paste(final_variables, collapse = "+"))), data = data)
-
-# Print the AIC value and final variables
-cat("AIC:", AIC(final_model), "\n")
-cat("Variables:", final_variables, "\n")
+kable(head(part2, 10), booktabs = TRUE, caption = "Part 2: Columns 9-16") %>%
+  kable_styling(latex_options = c("hold_position", "scale_down"))
 ```

### 2024-11-24 scripts/00-simulate_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Simulates the body fat data with columns: Pct.BF, Neck, Chest,
+# Purpose: Simulates the body fat data
   #Abdomen, Wrist, Weight
 # Author: Wendy Yuan
 # Date: 29 November 2024
@@ -7,32 +7,80 @@
 
 #### Workspace setup ####
 library(tidyverse)
-set.seed(304)
+set.seed(1009122423)
 
 #### Simulate Data ####
+# Mean and SD values are from the National Health and Nutrition Examination Survey and Anthropometric Data for U.S. Adults
+#variable, Mean(Approx.), Standard Deviation (Approx.)
+
+#Human Density (g/cm³)  1.05, 0.01
+#Pct.BF (%)             25,   10
+#Age                    40,   15
+#Weight (kg)            70,   15
+#Height (cm)            170,  10
+#Neck (cm)              37,   3
+#Chest (cm)             95,   10
+#Abdomen (cm)           85,   15
+#Waist (cm)             90,   12
+#Hip (cm)               95,   10
+#Thigh (cm)             55,   5
+#Knee (cm)              38,   3
+#Ankle (cm)             23,   2
+#Bicep (cm)             30,   5
+#Forearm (cm)           27,   3
+#Wrist (cm)             16,   1
 
 # Number of rows to simulate
 n <- 150
 
 # Simulate data for each column
-simulated_data <- tibble(
-  Pct.BF = runif(n, min = 5, max = 40),
-  Neck = rnorm(n, mean = 35, sd = 5),
-  Chest = rnorm(n, mean = 100, sd = 10),
-  Abdomen = rnorm(n, mean = 90, sd = 10),
-  Wrist = rnorm(n, mean = 18, sd = 2),
-  Weight = rnorm(n, mean = 70, sd = 15)
-)
+simulated_data <- NULL
 
-# Ensure no negative values
-simulated_data <- simulated_data %>%
-  mutate(
-    Neck = ifelse(Neck < 0, abs(Neck), Neck),
-    Chest = ifelse(Chest < 0, abs(Chest), Chest),
-    Abdomen = ifelse(Abdomen < 0, abs(Abdomen), Abdomen),
-    Wrist = ifelse(Wrist < 0, abs(Wrist), Wrist),
-    Weight = ifelse(Weight < 0, abs(Weight), Weight)
+repeat {
+  simulated_data <- tibble(
[…]

### 2024-11-24 scripts/01-test_simulated_data.R

@@ -25,11 +25,11 @@ if (nrow(sim_data) == 150) {
   stop("Test Failed: The dataset does not have 150 rows.")
 }
 
-# Test if the data has 6 columns (Pct.BF, Neck, Chest, Abdomen, Wrist, Weight)
-if (ncol(sim_data) == 6) {
-  message("Test Passed: The dataset has 6 columns.")
+# Test if the data has 16 columns
+if (ncol(sim_data) == 16) {
+  message("Test Passed: The dataset has 16 columns.")
 } else {
-  stop("Test Failed: The dataset does not have 6 columns.")
+  stop("Test Failed: The dataset does not have 16 columns.")
 }
 
 # Test if all columns contain numeric values
@@ -60,12 +60,19 @@ if (all(sim_data$Pct.BF >= 5 & sim_data$Pct.BF <= 40)) {
   stop("Test Failed: Some values in 'Pct.BF' are outside the range.")
 }
 
+# Test if all density values are between 0.9 and 1.1 (known minimum and maximum body density)
+if (all(sim_data$Density >= 0.9 & sim_data$Density <= 1.1)) {
+  message("Test Passed: All values in 'Density' are within the range (0.9, 1.1).")
+} else {
+  stop("Test Failed: Some values in 'Density' are outside the range.")
+}
+
 # Test if all values in body measurement columns are positive
-body_columns <- c("Neck", "Chest", "Abdomen", "Wrist", "Weight")
-if (all(sim_data %>% select(all_of(body_columns)) > 0)) {
+non_positive_cols <- names(sim_data)[sapply(sim_data, function(column) any(column <= 0))]
+if (length(non_positive_cols) ==0 ) {
   message("Test Passed: All body measurements are positive.")
 } else {
-  stop("Test Failed: Some body measurement values are not positive.")
+  stop(paste("Test Failed: Some values in '", paste(non_positive_cols, collapse = ", "), "' column(s) are not positive."))
 }
 
 # Test if all columns have variance (not constant)

### 2024-11-24 scripts/03-clean_data.R

@@ -14,7 +14,7 @@ library(tidyr)
 #### Clean data ####
 data <- read.table("data/01-raw_data/bodyfat.txt", header = TRUE, sep = "\t")
 
-# Handle missing values
+# Remove all missing values
 cleaned_data <- data %>% drop_na()
 
 # Remove duplicates
@@ -24,23 +24,39 @@ cleaned_data <- cleaned_data %>% distinct()
 lower_cutoff = 0.25
 upper_cutoff = 0.75
 
-# Function to remove outlines
+# Function to remove outlines, ensure all values are greater than 0
+epsilon = 1e-10
 remove_outliers <- function(data, column) {
   Q1 <- quantile(data[[column]], lower_cutoff, na.rm = TRUE)
   Q3 <- quantile(data[[column]], upper_cutoff, na.rm = TRUE)
   IQR <- Q3 - Q1
-  lower_bound <- Q1 - 1.5 * IQR
+  lower_bound <- max(Q1 - 1.5 * IQR, epsilon)
+  message(paste(column, ":", lower_bound))
   upper_bound <- Q3 + 1.5 * IQR
-  data %>%
-    filter(data[[column]] >= lower_bound & data[[column]] <= upper_bound)
+  
+  data %>% filter(data[[column]] >= lower_bound & data[[column]] <= upper_bound)
 }
 
 #Remove outliners by checking all columns
 for (column_name in colnames(cleaned_data)) {
   if (is.numeric(cleaned_data[[column_name]])) {
+    message(paste(column_name, " filtered"))
     cleaned_data <- remove_outliers(cleaned_data, column_name)
   }
 }
+
+# The original dataset includes weight in pounds, height and waist in inches, and body fat in g/m³. 
+# The remaining measurements are in centimeters. Normalize the units for the following columns:
+#lbs to kg (Keep two decimal places)
+cleaned_data$Weight <- cleaned_data$Weight * 0.453592
+cleaned_data$Weight <- floor(cleaned_data$Weight * 100) / 100
+
+#inch to cm (Keep two decimal places)
+cleaned_data$Height <- cleaned_data$Height * 2.54
+cleaned_data$Height <- floor(cleaned_data$Height * 100) / 100
+
+#inch to cm 
+cleaned_data$Waist <- cleaned_data$Waist * 2.54
 
 #### Save data ####
 write_parquet(cleaned_data, "data/02-analysis_data/bodyfat.parquet")

### 2024-11-26 paper/paper.qmd
wrote paper & updated llm

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Estimating Body Fat Using Circumference Measurements"
+subtitle: "Abdomen as the Strongest Predictor With Contributions From Wrist, Height, and Age For Affordable Health Monitoring"
 author: 
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This study uses a multi-linear regression model to estimate body fat percentage based on circumference measurements.
+Abdominal size was the strongest predictor, followed by wrist size, height, and age, which showed minimal contributions.
+These results demonstrate that accessible methods can effectively estimate body fat, offering methods suitable for non-clinical settings.
+This approach is important for identifying and managing health risks associated with extremely low or high body fat levels in a practical and affordable way."
 format: pdf
 number-sections: true
+toc: true
 bibliography: references.bib
@@
 
+\newpage
+
 # Introduction
 
-Why it matters paragraph
+Monitoring body fat is important because of the major role it plays in overall health.
+Current methods, like DXA scans and underwater weighing, are very reliable but often expensive, difficult to access, or only available in specialized facilities.
+More affordable methods, like using a measuring tape for body size, can provide reasonable estimates of body fat and are easier for more people to use [@measurement].
+A lack of easy and reliable ways to measure body fat can lead to missed chances to detect health risks.
+Excess body fat is strongly linked to conditions such as heart disease, type 2 diabetes, high blood pressure, and even certain cancers.
+It can also increase strain on the joints, leading to issues like osteoarthritis, and contribute to breathing problems like sleep apnea [@niddk].
+Extremely low body fat can interfere with key body functions, affecting hormone levels, immune health, and even heart rhythm.
+For example, not enough body fat can lead to irregular heartbeats, extreme fatigue, and reproductive issues [@lowbodyfat].
+Without proper tools to measure and manage body fat, individuals may unknowingly face these risks, making it important to research methods that are both reliable and affordable.
 
-Overview paragraph
+This study examines the reliability of using circumference measurements to estimate body fat.
+Starting with a dataset containing many measurements, we used backward selection to identify the most relevant variables impacting body fat.
+The four variables are: Age, Height, Abdomen, and Wrist circumference.
+After making sure these variables did not display collinearity, we tested the linear regression assumptions to confirm the model's validity.
+The selected variables were analyzed in a multiple linear regression model and individually in simple linear regression plots against body fat.
+This approach gives a clear understanding of how each variable relates to body fat.
+Finally, we evaluated the coefficients in the multiple regression model to make sure they aligned logically with the model, supporting its reliability.
 
-Results paragraph
+The study found that different body measurements had different effects on body fat percentage.
+Abdominal size had the strongest influence, with larger measurements strongly linked to higher body fat.
+Wrist size and height were associated with lower body fat, meaning that people with bigger wrists or greater height tend to have less fat overall.
+Age played a smaller role, with older individuals showing a slight tendency to have more body fat, but the effect was weaker than the other factors.
+Together, these measurements offered a practical way to estimate body fat, with abdominal size standing out as the most important factor.
 
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+The remainder of this paper is structured as follows: @sec-data explains the dataset source, how it was collected, and describes the variables used.
+@sec-model outlines the multi-linear regression setup and the rationale for its use.
+@sec-results presents the regression outcomes, showing how the predictors explain body fat percentage.
+@sec-discussion interprets the findings, notes limitations, and suggests improvements.
+@sec-appendix explores survey, sampling, and observational data methods, including measurement techniques, simulations.
 
@@
 
-Estimand paragraph
+The estimand of this study is body fat percentage, which we aim to estimate based on measurements from The Data And Story Library [@dasl].
+Body fat percentage is an important health metric that cannot be measured directly for every individual, especially outside of specialized settings.
+To address this, we used a multi-linear regression model, combining predictors such as age, height, abdomen, and wrist circumference to estimate body fat.
+By analyzing these variables, this study seeks to understand their effects on body fat.
+The model not only provides a framework for estimation making sure our approach is both structured and practical.
 
@@
 
-## Overview
-
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
-
-Overview text
-
 ## Measurement
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+This study uses the statistical programming language R [@citeR] and the packages: tidyverse  [@tidyverse], Arrow [@arrow], MASS [@mass], GGally [@ggally], gridExtra [@gridextra], Knitr [@knitr], kableExtra [@kableextra], Car [@car].
+The dataset used in this study, sourced from The Data And Story Library [@dasl], contains measurements on body fat percentage alongside various physical metrics for 250 male participants.
+The dataset was collected to analyze body fat as an important health measure, providing variables such as age, weight, height, and circumferences of specific body parts.
+These measurements were obtained through direct assessments to ensure accuracy and uniform input into the dataset.
+The dataset allows researchers to consider accessible ways to estimate body fat without relying on costly or specialized methods.
 
-cleaned data with normalized measurement 
+Before analysis, the raw dataset was cleaned to standardize and prepare the data for use.
+Since the original dataset included measurements in both inches and centimeters, all measurements were converted into centimeters to ensure uniformity, as detailed in [@tbl-cleaned1] & [@tbl-cleaned2].
+Additional cleaning steps included removing duplicates, addressing outliers, and removing missing observations to improve dataset’s usability.
+This cleaned data makes sure that the variables in the study are accurate and consistent.
+For reference, the original dataset before cleaning is provided in [@tbl-raw1] & [@tbl-raw2], showing the changes made during this process.
+
 ```{r}
+#| label: tbl-cleaned1
+#| tbl-cap: Cleaned Data of Body Fat Variables Part 1
 #| echo: false
@@
 # Render each part
-kable(head(part1, 10), booktabs = TRUE, caption = "Part 1: Columns 1-8") %>%
+kable(head(part1, 10), booktabs = TRUE) %>%
   kable_styling(latex_options = c("hold_position", "scale_down"))
+```
 
-kable(head(part2, 10), booktabs = TRUE, caption = "Part 2: Columns 9-16") %>%
+```{r}
+#| label: tbl-cleaned2
+#| tbl-cap: Cleaned Data of Body Fat Variables Part 2
+#| echo: false
+#| warning: false
+#| message: false
+
+kable(head(part2, 10), booktabs = TRUE) %>%
   kable_styling(latex_options = c("hold_position", "scale_down"))
@@
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
+The dependent variable in this study is percent body fat, which represents the proportion of an individual's total body mass that is composed of fat.
+This variable is a continuous measure and serves as the target outcome we aim to estimate using predictor variables.
+Percent body fat is an important indicator of health, as both excessive and extremely low levels can lead to various medical issues.
+In our analysis, understanding the distribution of this variable is essential for ensuring that it aligns with the assumptions required for linear regression modeling.
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+As shown in [@fig-pctbf], the histogram of percent body fat has a shape that is close to bell-like, though it is not perfectly symmetrical.
+Most individuals in the dataset have body fat levels clustered within a common range, with fewer individuals having much higher or much lower levels.
+There is a slight tendency for more values to stretch toward higher body fat percentages, creating a small imbalance in the shape of the distribution.
+The spread of values covers a wide range, reflecting the diversity in body fat levels across the individuals studied.
+At the extremes, a few outliers stand out - some with very low body fat and others with notably high levels.
 
 ```{r}
+#| label: fig-pctbf
+#| fig-cap: Distribution of Percent Body Fat
 #| echo: false
@@
 
-Talk more about it.
+\newpage
 
@@
 
-variables of interest: Age Height Abdomen Wrist
+The original uncleaned dataset contained the variables below:
 
-Reference appendix for how variables were picked using backward selection method
+- Density: The measure of body density, used as a key variable in estimating body fat percentage. It combines body weight and volume to provide insights into overall composition.
+- Age: The age of the individual in years, providing a measure of the person's stage of life, which can influence body composition.
+- Weight: The total body mass of the individual, reflecting the combined weight of bones, muscles, fat, and other tissues.
+- Height: The standing height of the individual, often used alongside weight to calculate proportions and indices like BMI.
+- Neck: The circumference of the neck, offering a measurement of fat and muscle distribution in the upper body.
+- Chest: The circumference of the chest, reflecting the size and structure of the upper torso, including muscle and fat.
+- Abdomen: The circumference around the abdomen, a key indicator of central fat distribution and a significant predictor of body fat percentage.
+- Waist: The measurement around the waist, often used with hip circumference to assess body shape and fat distribution.
+- Hip: The circumference of the hips, providing a measure of lower-body proportions and often paired with waist circumference to calculate ratios.
+- Thigh: The circumference of the thigh, measured to understand muscle and fat distribution in the upper leg.
+- Knee: The circumference of the knee, offering additional detail about lower-body structure and proportions.
+- Ankle: The measurement around the ankle, reflecting skeletal and soft tissue composition in the lower leg.
+- Bicep: The circumference of the bicep, measured with the arm flexed, highlighting upper-arm muscle and fat distribution.
+- Forearm: The circumference of the forearm, providing information about the composition of the lower arm.
+- Wrist: The circumference of the wrist, a useful proxy for skeletal size and overall body frame.
 
-Add graphs, tables and text.
-
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
+To focus on the most important variables, this study used backward selection to find the four that gave the best model fit, with the lowest Akaike Information Criterion (AIC).
+Backward selection works by starting with all the variables and gradually removing those that add the least to explaining body fat percentage, based on statistical rules.
+This process ensures the final set of variables is strongly related to the outcome.
+As shown in [@fig-aic], this approach narrowed the variables down to Age, Height, Abdomen, and Wrist circumference.
+These four were chosen because they worked together to provide the best explanation of the differences in body fat levels while keeping the model simple and effective.
 
 ```{r}
+#| label: fig-aic
+#| fig-cap: AIC Optimizing Best 4 Variables 
 #| echo: false
@@
 # Print the AIC value and final variables
-cat("AIC:", AIC(final_model), "\n")
-cat("Variables:", final_variables, "\n")
+kable(final_variables)
 ```
+
+The histograms of Age, Height, Abdomen, and Wrist shown in [@fig-predictor] explain their role in predicting body fat.
+Most participants are between 30 and 60 years old, with fewer older individuals, making the sample mainly middle-aged.
+Height is evenly spread and follows a balanced shape, making it a reliable variable for the analysis.
+Abdomen size is mostly within a common range, with a few larger measurements that could influence the results due to their link to higher body fat.
+Wrist size has less variation but is consistent and still important because of its connection to lower body fat.
+Overall, these variables work well for modeling body fat, although the uneven spread of Age might need adjustments for better results.
 
@@
 #| message: false
+#| label: fig-predictor
+#| fig-cap: Distributions of Age, Height, Abdomen, Wrist
 
@@
 hist(data$Age, main = "Histogram of Age", xlab = "Age", col = "#7dbeff", border = "black")
-hist(data$Height, main = "Histogram of Height", xlab = "Height (inches)", col = "#2aebaa", border = "black")
+hist(data$Height, main = "Histogram of Height", xlab = "Height (cm)", col = "#2aebaa", border = "black")
 hist(data$Abdomen, main = "Histogram of Abdomen", xlab = "Abdomen (cm)", col = "#eb49a4", border = "black")
@@
 
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-
-model <- lm(Pct.BF ~ Age + Height + Abdomen + Wrist, data = data)
-
-# Calculate VIF
-vif_values <- vif(model)
-
-# Print VIF values
-print(vif_values)
-```
-
-# Model
-
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
-
-## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
-
-$y_i = \beta_0 + \beta_1 x_{1i} + \beta_2 x_{2i} + \beta_3 x_{3i} + \beta_4 x_{4i}$
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-### Model justification
-
-Linear reg assumptions
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-
-# Fit the linear regression model
-model <- lm(Pct.BF ~ Age + Height + Abdomen + Wrist, data = data)
-
-# 1. Linearity: Residuals vs Fitted Plot
-plot(model$fitted.values, residuals(model), 
-     main = "Residuals vs Fitted",
-     xlab = "Fitted Values",
-     ylab = "Residuals")
-abline(h = 0, col = "red")
-```
+The pairwise plot, [@fig-pairwise], shows how Age, Height, Abdomen, and Wrist are related to each other.
+Abdomen and Wrist have the strongest relationship.
+Larger abdominal circumferences are generally linked to larger wrists, showing overall body size.
+Age has a weak connection to Abdomen.
+Older individuals tend to have slightly larger abdominal sizes.
+However, Age shows no clear relationship with Height or Wrist.
+Height has small links to both Abdomen and Wrist.
+Taller individuals tend to have slightly smaller abdominal sizes and larger wrists.
+Abdomen and Wrist are the most important variables for predicting body fat.
+Height and Age provide smaller, additional contributions.
+The lack of strong correlations between these variables means they work well together in a regression model.
 
 ```{r}
-#| echo: false
-#| warning: false
-#| message: false
-
-# 2. Independence: Durbin-Watson Test (requires car package)
-# install.packages("car")  # Uncomment to install if not already installed
-library(car)
-durbinWatsonTest(model)
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-
-# 3. Homoscedasticity: Scale-Location Plot
-plot(model, which = 3)
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-
-# 4. Normality: Q-Q Plot of Residuals
-qqnorm(residuals(model))
-qqline(residuals(model), col = "red")
-```
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
-# Results
-
-Our results are summarized in @tbl-modelresults.
-
-Multicollinear between picked vars 
-```{r}
+#| label: fig-pairwise
+#| fig-cap: Pairwise Plot Compairing the Relationship Between Age, Heigh, Abdomen, Wrist
 #| echo: false
@@
 
+The variance inflation factor (VIF) is used to check if the predictors in a regression model are too closely related, a problem called multicollinearity.
+VIF shows how much a predictor’s contribution is influenced by its relationship with other variables.
+A VIF of 1 means no overlap, while values over 5 or 10 might cause issues and need fixing.
+
+[@fig-vif] shows the VIF values for Age, Height, Abdomen, and Wrist are all below 2 - meaning there is very little overlap between them.
+Wrist has the highest value (1.724), but this is still low, meaning it is only slightly related to other variables.
+The scatterplots showed some small relationships between variables, and the VIF confirms that these are not strong enough to cause problems.
+This means each variable adds its own useful information to the model.
+
 ```{r}
+#| label: fig-vif
+#| fig-cap: VIF Values of Age, Height, Abdomen, Wrist
+#| echo: false
+#| warning: false
+#| message: false
+
+model <- lm(Pct.BF ~ Age + Height + Abdomen + Wrist, data = data)
+
+# Calculate VIF
+vif_values <- vif(model)
+
+# Print VIF values
+kable(vif_values)
+```
+
+# Model {#sec-model}
+
+The goal of our model is to estimate body fat percentage using four predictors: Age, Height, Abdomen, and Wrist circumference.
+This helps us understand how each variable affects body fat while making sure the model gives accurate estimates.
+
+\newpage
+
+## Model set-up
+
+Define $y_i$ as the body fat percentage for the $i$-th individual. The predictors in the model are:
+
+- $x_{1i}$: Age, representing the individual’s age in years.
+- $x_{2i}$: Height, measured in centimeters.
+- $x_{3i}$: Abdomen, the abdominal circumference in centimeters.
+- $x_{4i}$: Wrist, the wrist circumference in centimeters.
+
+The model is expressed as:
+
+$y_i = \beta_0 + \beta_1 x_{1i} + \beta_2 x_{2i} + \beta_3 x_{3i} + \beta_4 x_{4i}$
+
+where $\beta_0$ is the intercept, $\beta_1, \beta_2, \beta_3, \beta_4$ are the coefficients for each predictor, and $\epsilon_i$ represents the error term, assumed to be normally distributed with mean 0.
+Diagnostic plots and residual checks were performed to assess whether the model passed linear regression assumptions
+
+### Model justification
+
+Linear regression has four key assumptions to ensure the model works well.
+Linearity means the relationship between the predictors and the outcome should be straight, so the model captures the correct pattern.
+Constance variance means the residuals should have the same spread across all predictor variables.
+Normality requires the errors to follow a normal distribution.
+Independence ensures the errors are not related to each other, avoiding bias.
+Checking these assumptions helps make sure the model is accurate and trustworthy.
+
+The residual plot, shown in [@fig-residual], helps assess both the linearity and independence assumptions in the linear regression model.
+There is no strong curve or trend in the residuals, confirming that the linearity assumption holds well.
+The residuals are randomly scattered around the red horizontal line at zero, with no noticeable patterns or clustering, indicating that the model correctly captures the relationships between the predictors and the dependent variable.
+This randomness also suggests that the residuals are independent, as they are not systematically related to each other or to the fitted values.
+Together, these results confirm that the model satisfies both the linearity and independence assumptions, providing a solid basis for interpreting the results.
+
+```{r}
+#| label: fig-residual
+#| fig-cap: Residual Plot Verifying the Linearity Assumption
+#| echo: false
+#| warning: false
+#| message: false
+
+# Fit the linear regression model
+model <- lm(Pct.BF ~ Age + Height + Abdomen + Wrist, data = data)
+
+# 1. Linearity: Residuals vs Fitted Plot
+plot(model$fitted.values, residuals(model), 
+     main = "Residuals vs Fitted",
+     xlab = "Fitted Values",
+     ylab = "Residuals")
+abline(h = 0, col = "red")
+```
+
+The Scale-Location plot, [@fig-variance], is used to assess the assumption of constant variance in a linear regression model.
+The standardized residuals are plotted against the fitted values, with the red line representing the trend.
+For the assumption of constant variance to hold, the points should be scattered randomly around the red line without forming a pattern or a funnel shape.
+In this plot, the points seem to be spread out evenly across the predicted values, with no clear signs of the spread getting bigger or smaller.
+This means the errors have a consistent variance confirming the linear regression assumption.
+
+```{r}
+#| label: fig-variance
+#| fig-cap: Scale Location Verifying Constance Variance Assumption
+#| echo: false
+#| warning: false
+#| message: false
+
+plot(model, which = 3)
+```
+
+The Normal Q-Q plot, [@fig-normality] checks if the residuals (errors) in the model follow a normal distribution.
+If the errors are normal, the points should stay close to the red line.
+Here, most points are close to the line, meaning the errors are roughly normal.
+At the ends, some points are farther from the line, which might mean there are some extreme values or outliers.
+Overall, the errors seem mostly normal satisfying the linear regression assumption.
+
+```{r}
+#| label: fig-normality
+#| fig-cap: QQ-Plot Verifying the Normality of Errors Assumption
+#| echo: false
+#| warning: false
+#| message: false
+
+# 4. Normality: Q-Q Plot of Residuals
+qqnorm(residuals(model))
+qqline(residuals(model), col = "red")
+```
+
+We expect larger body measurements to be linked to higher body fat percentages.
+Specifically, people with bigger abdominal or wrist circumferences are likely to have more body fat.
+Abdomen size often shows how much fat is stored in the center of the body, which contributes a lot to total body fat.
+Wrist circumference, while less variable, can reflect overall body size and fat distribution.
+In contrast, we expect taller individuals to have less body fat because taller people usually have leaner body compositions.
+
+We also expect older individuals to have slightly more body fat.
+As people age, changes in metabolism and lifestyle can lead to gradual increases in fat.
+By using these variables in a multi-linear regression model, we can measure how each one affects body fat percentage.
+For example, the model will estimate how much body fat percentage increases when abdomen size grows by one unit, while keeping the other variables unchanged.
+This helps us understand the role of each measurement in predicting body fat.
+
+# Results {#sec-results}
+
+The scatterplots from [@fig-simple] provide an initial look at the relationships between body fat percentage and the variables: Age, Height, Abdomen, and Wrist circumference.
+It looks at whether trends exist between the dependent variable and the predictors, giving a sense of how each variable may contribute to the model.
+
+- Pct.BF vs Age: There is a slight positive trend, indicating that body fat percentage tends to increase as Age increases.
+While this relationship is not very strong, it suggests age could have a modest impact on body fat.
+- Pct.BF vs Height: The plot shows no clear trend, with a nearly flat line indicating that Height likely has little influence on body fat percentage.
+- Pct.BF vs Abdomen: A strong positive relationship is visible, as body fat percentage increases significantly with Abdomen circumference.
+This suggests Abdomen size is a key predictor of body fat due to its role in central fat storage.
+- Pct.BF vs Wrist: A weak negative trend is observed, suggesting that individuals with larger Wrist circumferences tend to have slightly lower body fat percentages.
+
+```{r}
+#| label: fig-simple
+#| fig-cap: Simple Linear Regression Plots Against Body Fat Percent for Age, Height, Abdomen, Wrist
 #| echo: false
@@
 
+The regression results are summarized in [@tbl-multi].
+The intercept, which represents the estimated body fat percentage when all predictors are zero, is 2.01.
+However, this value doesn't have much real-world meaning because variables like height and abdomen size cannot actually be zero.
+Among the predictors, Abdomen circumference has the strongest positive effect on body fat percentage.
+For every 1 cm increase in abdomen size, body fat percentage increases by about 0.78%, while keeping other factors unchanged.
+
+Wrist circumference shows a significant negative relationship with body fat percentage.
+This means that people with larger wrists tend to have lower body fat percentages.
+Height also has a small negative effect, indicating that taller individuals are likely to have slightly lower body fat.
+Age has a weak positive effect, meaning body fat percentage may slightly increase with age, but this result is less certain.
+
+The model explains about 70.3% of the variation in body fat percentage, showing it fits the data well.
+The residual standard error is 4.33, meaning the model's predictions are fairly accurate on average.
+Overall, Abdomen and Wrist are the most important predictors, with Height and Age playing smaller roles.
+Abdomen circumference stands out as the strongest factor for estimating body fat percentage.
+
 ```{r}
+#| label: tbl-multi
+#| tbl-cap: Multi-linear Regression Model
 #| echo: false
@@
 
+## Model Validation
+
+The plot, [@fig-coefficients] verifies the reliability of the multi-linear regression model by showing the estimated effects of each predictor and their 90% confidence intervals.
+It confirms that the model’s results are consistent and aligns with key assumptions of linear regression.
+
+- Abdomen: The strong positive coefficient and confidence interval far from zero confirm that Abdomen is a significant predictor of body fat percentage.
+This shows the model correctly identifies meaningful relationships between predictors and the dependent variable.
+- Wrist: The negative coefficient and confidence interval that does not cross zero confirm that the model captures the relationship between Wrist size and lower body fat.
+While the interval for Wrist is slightly wider, it still supports the model’s reliability.
+- Height: The negative coefficient with a confidence interval just avoiding zero confirms the model captures a small but reliable relationship between Height and body fat percentage.
+- Age: The confidence interval for Age includes zero, confirming the model’s result that Age has a weaker and statistically insignificant effect on body fat percentage.
+
 ```{r}
+#| label: fig-coefficients
+#| fig-cap: Model Coefficients Confidence Intervals
 #| echo: false
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 
-## First discussion point {#sec-first-point}
+## Best Predictor: Abdomen
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+The regression results confirm that abdomen circumference is the strongest predictor of body fat percentage, with a coefficient of 0.784 and a highly significant p-value (<2e-16).
+This means that for every 1 cm increase in abdomen size, body fat percentage increases by approximately 0.78%, holding all other variables constant.
+Abdomen size is directly related to fat accumulation around the central part of the body, which is often linked to overall body fat levels.
+This finding aligns with the understanding that abdominal fat is a strong indicator of general adiposity and health risks, such as heart disease and metabolic disorders.
+The importance of abdomen as a predictor highlights its role in practical applications of body fat estimation models, particularly for tracking health outcomes and identifying individuals at risk for fat-related conditions.
 
-## Second discussion point
+## Contributions of Wrist and Height
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
+The results also show meaningful contributions from wrist circumference and height, though their relationships with body fat differ.
+Wrist circumference has a significant negative coefficient (-1.942, p = 2.38e-05), indicating that individuals with larger wrists tend to have lower body fat percentages.
+This could reflect differences in body structure, where a larger wrist size often suggests a higher proportion of bone mass compared to fat mass.
+Height, on the other hand, has a smaller negative coefficient (-0.123, p = 0.0169), showing that taller individuals generally have slightly lower body fat percentages.
+This relationship may stem from taller individuals having a larger lean body mass proportion relative to their overall size.
+These results suggest that, while Abdomen plays the main role, Wrist and Height provide important context in understanding body fat distribution.
+They highlight the need to consider body structure, not just size, when evaluating fat levels.
 
-## Third discussion point
+## Model Fit and Predictive Strength
 
-## Weaknesses and next steps
+The model demonstrates strong predictive ability, with an R^2 value of 0.7033 and an adjusted R^2 of 0.698.
+This means that approximately 70% of the variation in body fat percentage is explained by the four predictors in the model: Age, Height, Abdomen, and Wrist.
+The residual standard error of 4.33 indicates that the model's predictions are reasonably close to the actual values, with only a small degree of error.
+While Abdomen is a primary predictor, and Wrist and Height also contribute, Age appears to be a weaker predictor.
+Its coefficient (0.046) has a p-value of 0.071, indicating it is not statistically significant at the 5% level.
+This suggests that while body fat percentage might slightly increase with age, the relationship is not strong enough to rely on for predictive purposes.
+Including Age adds only marginal value to the model, and its role is less important compared to the other predictors.
+These results validate the model’s usefulness in estimating body fat and emphasize its role in applications such as health monitoring, where accessible and reliable measurement tools are needed.
 
-Weaknesses and next steps should also be included.
+# Weaknesses and Next Steps
 
-# Conclusion
+This paper creates a multi-linear regression model to estimate body fat percentage using four predictors: Age, Height, Abdomen, and Wrist circumference.
+The dataset includes male participants, and the study ensures the model follows linear regression assumptions.
+The results show how each predictor contributes to body fat percentage, with Abdomen being the most important factor.
+
+One finding is that abdominal size is a strong predictor of body fat percentage.
+This supports the idea that fat stored in the abdominal area plays a main role in overall body fat levels.
+Abdomen circumference serves as a useful and accessible measure for monitoring body fat, making it helpful for health-related purposes.
+
+We also learn that structural factors like wrist size are connected to body fat percentage.
+Larger wrists are linked to lower body fat, possibly because of a higher proportion of bone mass compared to fat mass.
+This finding shows the need to consider body structure, not just size, when assessing body fat.
+
+### Weaknesses
+
+One issue with this study is that the data only includes men, making it difficult to apply the findings to other groups, such as women or people from different backgrounds.
+Body fat distribution and its predictors vary by gender and other factors, which limits how useful the model is for the general population.
+The dataset also focuses mostly on people aged 30 to 60, with very few younger or older individuals.
+As a result, the model may not work well for teenagers, young adults, or seniors, who might have different patterns of body fat.
+
+Another limitation is the number of predictors used.
+The model includes Age, Height, Abdomen, and Wrist but leaves out others like weight, hip size, and thigh size, which could improve predictions.
+These variables were excluded during backward selection to simplify the model, but some of them might still be important.
+Excluding these predictors could make the model less accurate in explaining body fat differences across individuals.
+
+The residual analysis also showed minor issues.
+While the model works well overall, there are some outliers and slight deviations from normality in the residuals.
+These could affect how well the model predicts body fat for people with very high or very low values.
+Additionally, the residual patterns suggest there might be other predictors not included in the model that could explain some of the remaining variability.
+
+### Future Steps
+
+Future research should focus on expanding the dataset to include more diverse groups.
+Adding data for women and people from different backgrounds would make the model more useful for a wider population.
+Including people of all ages, especially teenagers and seniors, would help the model predict body fat for everyone, not just middle-aged adults.
+A more balanced dataset would also make it easier to detect patterns that apply to specific groups.
+
+Researchers should also consider adding more predictors to the model.
+Including variables like weight, hip size, and thigh size could give a fuller picture of body fat distribution and improve the model’s accuracy.
+Looking at how important each variable is could help decide which ones to add while keeping the model manageable.
+
+Finally, using different methods to model the data could address some of the limitations.
+For example, machine learning techniques or non-linear models could find patterns that linear regression might miss, especially for outliers.
+Future studies could also use data collected over time to see how body fat changes as people age and whether the same predictors still apply.
+This would help create a better understanding of body fat and how it changes throughout life.
 
@@
 
-# Appendix {-}
+# Appendix {#sec-appendix}
+
+## Appendix A
 
 ```{r}
+#| label: tbl-raw1
+#| tbl-cap: Raw Data of Body Fat Variables Part 1
 #| echo: false
@@
 # Render each part
-kable(head(part1, 10), booktabs = TRUE, caption = "Part 1: Columns 1-8") %>%
-  kable_styling(latex_options = c("hold_position", "scale_down"))
-
-kable(head(part2, 10), booktabs = TRUE, caption = "Part 2: Columns 9-16") %>%
+kable(head(part1, 10), booktabs = TRUE) %>%
   kable_styling(latex_options = c("hold_position", "scale_down"))
 ```
+
+```{r}
+#| label: tbl-raw2
+#| tbl-cap: Raw Data of Body Fat Variables Part 2
+#| echo: false
+#| warning: false
+#| message: false
+
+kable(head(part2, 10), booktabs = TRUE) %>%
+  kable_styling(latex_options = c("hold_position", "scale_down"))
+```
+
+## Appendix B
 

### 2024-11-26 paper/paper.qmd
updated references

@@
 
+This study uses the statistical programming language R [@citeR] and the packages: tidyverse  [@tidyverse], Arrow [@arrow], MASS [@mass], GGally [@ggally], gridExtra [@gridextra], Knitr [@knitr], kableExtra [@kableextra], Car [@car], TestThat [@testthat], dplyr [@dplyr], readr [@readr], tidyr [@tidyr].
+
 ## Measurement
 
-This study uses the statistical programming language R [@citeR] and the packages: tidyverse  [@tidyverse], Arrow [@arrow], MASS [@mass], GGally [@ggally], gridExtra [@gridextra], Knitr [@knitr], kableExtra [@kableextra], Car [@car].
 The dataset used in this study, sourced from The Data And Story Library [@dasl], contains measurements on body fat percentage alongside various physical metrics for 250 male participants.
@@
 For reference, the original dataset before cleaning is provided in [@tbl-raw1] & [@tbl-raw2], showing the changes made during this process.
+
+\newpage
 
@@
 ```
-
-\newpage
 
@@
 This helps us understand how each variable affects body fat while making sure the model gives accurate estimates.
-
-\newpage
 

### 2024-12-01 scripts/00-simulate_data.R
made new script files for exploring variables

@@ -10,7 +10,9 @@ library(tidyverse)
 set.seed(1009122423)
 
 #### Simulate Data ####
-# Mean and SD values are from the National Health and Nutrition Examination Survey and Anthropometric Data for U.S. Adults
+# Mean and SD values are from the National Health and Nutrition Examination 
+# Survey and Anthropometric Data for U.S. Adults
+
 #variable, Mean(Approx.), Standard Deviation (Approx.)
 
 #Human Density (g/cm³)  1.05, 0.01

### 2024-12-01 scripts/01-test_simulated_data.R

@@ -60,19 +60,24 @@ if (all(sim_data$Pct.BF >= 5 & sim_data$Pct.BF <= 40)) {
   stop("Test Failed: Some values in 'Pct.BF' are outside the range.")
 }
 
-# Test if all density values are between 0.9 and 1.1 (known minimum and maximum body density)
+# Test if all density values are between 0.9 and 1.1 (known minimum and maximum
+# body density)
 if (all(sim_data$Density >= 0.9 & sim_data$Density <= 1.1)) {
-  message("Test Passed: All values in 'Density' are within the range (0.9, 1.1).")
+  message(paste("Test Passed: All values in 'Density' are within the range",
+                "(0.9, 1.1)."))
 } else {
   stop("Test Failed: Some values in 'Density' are outside the range.")
 }
 
 # Test if all values in body measurement columns are positive
-non_positive_cols <- names(sim_data)[sapply(sim_data, function(column) any(column <= 0))]
-if (length(non_positive_cols) ==0 ) {
+non_positive_cols <- names(sim_data)[sapply(sim_data, function(column) 
+  any(column <= 0))]
+if (length(non_positive_cols) == 0 ) {
   message("Test Passed: All body measurements are positive.")
 } else {
-  stop(paste("Test Failed: Some values in '", paste(non_positive_cols, collapse = ", "), "' column(s) are not positive."))
+  stop(paste("Test Failed: Some values in '", paste(non_positive_cols, 
+                                                    collapse = ", "),
+             "' column(s) are not positive."))
 }
 
 # Test if all columns have variance (not constant)

### 2024-12-01 scripts/03-clean_data.R

@@ -45,8 +45,10 @@ for (column_name in colnames(cleaned_data)) {
   }
 }
 
-# The original dataset includes weight in pounds, height and waist in inches, and body fat in g/m³. 
-# The remaining measurements are in centimeters. Normalize the units for the following columns:
+# The original dataset includes weight in pounds, height and waist in inches, 
+# and body fat in g/m³. The remaining measurements are in centimeters. 
+# Normalize the units for the following columns:
+
 #lbs to kg (Keep two decimal places)
 cleaned_data$Weight <- cleaned_data$Weight * 0.453592
 cleaned_data$Weight <- floor(cleaned_data$Weight * 100) / 100

### 2024-12-01 scripts/04-test_analysis_data.R

@@ -12,8 +12,9 @@ library(testthat)
 library(arrow)
 library(dplyr)
 
-# Load the cleaned dataset
-cleaned_data <- read_parquet("data/02-analysis_data/bodyfat.parquet")
+# Load the cleaned dataset, the test starts in scripts folder, use relative 
+# path to find data folder.
+cleaned_data <- read_parquet(here::here("data/02-analysis_data/bodyfat.parquet"))
 
 #### Test cleaned data ####
 
@@ -40,4 +41,14 @@ test_that("no missing values in dataset", {
 # Test that there are no duplicate rows
 test_that("no duplicate rows in dataset", {
   expect_equal(nrow(cleaned_data), nrow(distinct(cleaned_data)))
+})
+
+# Test that all values are greater than zero
+test_that("All values are greater than zero", {
+  expect_true(all(cleaned_data > 0))
+})
+
+# Test that all age values are integer
+test_that("All age values are integer", {
+  expect_true(all.equal(cleaned_data$Age, as.integer(cleaned_data$Age)))
 })

### 2024-12-01 scripts/05-exploratory_data_analysis.R

@@ -1,0 +1,45 @@
+#### Preamble ####
+# Purpose: Exploratory data analysis on variables
+# Author: Wendy Yuan
+# Date: 29 November 2024
+# Contact: w.yuan@mail.utoronto.ca 
+# Pre-requisites: 
+# - 03-clean_data.R must have been run
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(arrow)
+library(MASS)
+library(knitr)
+
+#### Read data ####
+data <- read_parquet("data/02-analysis_data/bodyfat.parquet")
+data <- data[ , !(names(data) %in% c("Density"))]
+
+# Full model using all variables except Density
+full_model <- lm(Pct.BF ~ ., data = data)
+
+# Perform backward selection
+backward_model <- stepAIC(full_model, direction = "backward", trace = 0)
+
+# Extract the final 4-variable model
+final_variables <- names(coef(backward_model))[-1] # Exclude intercept
+while (length(final_variables) > 4) {
+  current_model <- lm(as.formula(paste("Pct.BF ~",
+                          paste(final_variables, collapse = "+"))), data = data)
+  current_aic <- AIC(current_model)
+  
+  # Drop one variable at a time and calculate AIC
+  aic_values <- sapply(final_variables, function(var) {
+    temp_model <- lm(as.formula(paste("Pct.BF ~", paste(setdiff(
+      final_variables, var), collapse = "+"))), data = data)
+    return(AIC(temp_model))
+  })
+  
+  # Remove the variable leading to the lowest AIC improvement
+  final_variables <- setdiff(final_variables, names(which.min(aic_values)))
+}
+
+# Print the AIC value and final variables
+kable(final_variables)

### 2024-12-01 scripts/06-model_data.R

@@ -1,0 +1,22 @@
+#### Preamble ####
+# Purpose: Build final model
+# Author: Wendy Yuan
+# Date: 29 November 2024
+# Contact: w.yuan@mail.utoronto.ca 
+# Pre-requisites: 
+# - 05-exploratory-data_analysis.R must have been run
+
+library(arrow)
+
+# Final variables learned from 05-exploratory-data_analysis.R
+final_variables <- c( "Age", "Height", "Abdomen", "Wrist" )
+
+data <- read_parquet( "data/02-analysis_data/bodyfat.parquet" )
+
+# Final 4-variable model
+final_model <- lm( as.formula(paste("Pct.BF ~", 
+                        paste(final_variables, collapse = "+"))), data = data )
+summary(final_model)
+
+#### Save model ####
+saveRDS(final_model, file = "data/03-model_data/final_model.rds")

### 2024-12-01 other/datasheet/datasheet.qmd
finished appendix b & updated readme

---
title: "Datasheet for 'Body Fat Percentage Dataset'"
subtitle: "My subtitle if needed"
author: 
  - Wendy Yuan
thanks: "Code and data are available at: https://github.com/kiwindyy/Body-Fat"
date: November 29, 2024
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
# bibliography: references.bib
---

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to enable analysis of Australian politicians. We were unable to find a publicly available dataset in a structured format that had the biographical and political information on Australian politicians that was needed for modelling.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - TBD
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - TBD
4. *Any other comments?*
    - TBD

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- TBD
2. *How many instances are there in total (of each type, if appropriate)?*
	- TBD
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- TBD
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- TBD
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- TBD
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- TBD
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- TBD
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- TBD
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- TBD
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- TBD
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- TBD
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- TBD
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- TBD
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- TBD
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- TBD
16. *Any other comments?*
	- TBD

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- TBD
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- TBD
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- TBD
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- TBD
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- TBD
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- TBD
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- TBD
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- TBD
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- TBD
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
12. *Any other comments?*
	- TBD

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- TBD
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- TBD
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- TBD
4. *Any other comments?*
	- TBD

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- TBD
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- TBD
3. *What (other) tasks could the dataset be used for?*
	- TBD
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- TBD
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- TBD
6. *Any other comments?*
	- TBD

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- TBD
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- TBD
3. *When will the dataset be distributed?*
	- TBD
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- TBD
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- TBD
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- TBD
7. *Any other comments?*
	- TBD

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- TBD
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- TBD
3. *Is there an erratum? If so, please provide a link or other access point.*
	- TBD
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- TBD
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- TBD
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- TBD
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- TBD
8. *Any other comments?*
	- TBD

\newpage

# References

### 2024-12-01 paper/paper.qmd
finished appendix b & updated readme

@@
 @sec-discussion interprets the findings, notes limitations, and suggests improvements.
-@sec-appendix explores survey, sampling, and observational data methods, including measurement techniques, simulations.
+@sec-a is the raw dataset before any cleaning.
+@sec-b explores survey, sampling, and observational data methods, including measurement techniques, simulations.
 
@@
 This cleaned data makes sure that the variables in the study are accurate and consistent.
-For reference, the original dataset before cleaning is provided in [@tbl-raw1] & [@tbl-raw2], showing the changes made during this process.
+For reference, the original dataset before cleaning is provided in [@tbl-raw1] & [@tbl-raw2] in @sec-a, showing the changes made during this process.
 
@@
 
-The regression results are summarized in [@tbl-multi].
+The regression results are summarized in [@tbl-multi1], showing the coefficients and pvalues & [@tbl-multi2], showing the $R^2$ and standard error.
 The intercept, which represents the estimated body fat percentage when all predictors are zero, is 2.01.
@@
 ```{r}
-#| label: tbl-multi
-#| tbl-cap: Multi-linear Regression Model
+#| label: tbl-multi1
+#| tbl-cap: Multi-linear Regression Model Coefficients & P-Values
 #| echo: false
@@
 model <- lm(Pct.BF ~ Age + Height + Abdomen + Wrist, data = data)
-summary(model)
+model_summary <- summary(model)
+
+# Extract coefficients and p-values
+coefficients_table <- data.frame(
+  Variable = rownames(model_summary$coefficients),
+  Estimate = model_summary$coefficients[, "Estimate"],
+  `P-Value` = model_summary$coefficients[, "Pr(>|t|)"],
+  row.names = NULL
+)
+
+kable(coefficients_table)
+```
+
+```{r}
+#| label: tbl-multi2
+#| tbl-cap: Multi-linear Regression Model R-squared & RSE 
+#| echo: false
+#| warning: false
+#| message: false
+
+# Add residual standard error, R-squared, and adjusted R-squared
+model_stats <- data.frame(
+  Metric = c("Residual Standard Error", "Multiple R-squared", "Adjusted R-squared"),
+  Value = c(
+    model_summary$sigma,
+    model_summary$r.squared,
+    model_summary$adj.r.squared
+  )
+)
+
+kable(model_stats)
 ```
@@
 
-The model demonstrates strong predictive ability, with an R^2 value of 0.7033 and an adjusted R^2 of 0.698.
+The model demonstrates strong predictive ability, with an $R^2$ value of 0.7033 and an adjusted $R^2$ of 0.698.
 This means that approximately 70% of the variation in body fat percentage is explained by the four predictors in the model: Age, Height, Abdomen, and Wrist.
@@
 
-# Appendix {#sec-appendix}
+# Raw Data of Body Fat Percentage {#sec-a}
 
-## Appendix A
+## First 8 Variables
 
@@
 
+## Final 8 Variables
+
 ```{r}
@@
 
-## Appendix B
+# Surveys, sampling, and observational data {#sec-b}
+
+## Similar Methodologies From Literature
+
+***Overview of Related Methods***
+
+The study by @potter, Circumference-Based Predictions of Body Fat Revisited, analyzed the use of abdominal circumference measurements to estimate body fat percentage.
+This method, used by the United States Marine Corps, was compared against dual-energy X-ray absorptiometry, a standard reference, and bioelectrical impedance analysis to evaluate its accuracy.
+The sample included 609 Marines, consisting of 430 men and 179 women, aged 18–57 years, and the study looked at differences in results by gender and age.
+
+***Strengths of the Study***
+
+The study found that abdominal circumference is a practical predictor of body fat percentage in men, particularly when their body fat percentage is within the range expected for military fitness standards (18–26%) [@potter].
+The method’s simplicity and low cost make it suitable for widespread use in military settings where assessments need to be performed efficiently.
+By including men and women from different age groups, the study provided a broad view of how the method performs across a variety of individuals who meet Marine Corps fitness standards.
+The study also addressed the relationship between age and body fat.
+Older individuals tended to have slightly more fat mass but similar fat-free mass compared to younger participants.
+This suggests the method is generally consistent across age groups in terms of patterns of underestimation or overestimation.
+
+***Limitations of the Study***
+
+However, the study also highlighted significant limitations [@potter].
+The method underestimated body fat percentage in men by an average of 2.6 percent, while it overestimated body fat in women by 2.3 percent for younger participants and 1.3 percent for older participants.
+These differences were due to variations in fat distribution.
+Women often store fat in areas not measured by abdominal circumference, such as the hips and thighs, leading to overestimations.
+For men, especially those with lower body fat, the method struggled to account for intra-abdominal fat, resulting in underestimations.
+The study also tested bioelectrical impedance analysis, which was more accurate overall but still affected by errors in individuals with extreme body fat percentages and by hydration variability.
+Both methods were found to lack the precision needed for detailed body composition assessments.
+
+***Comparison to This Paper***
+
+This paper builds on @potter work by addressing some of the identified shortcomings.
+For example, while @potter focused solely on abdominal circumference, this study incorporates additional variables, such as wrist size and height, into a statistical model.
+These extra measurements aim to make predictions more accurate, especially for individuals at the lower or higher ends of the body fat range.
+
+Additionally, @potter highlighted that body fat is distributed differently between genders.
+This study focuses only on middle-aged men.
+By concentrating on this group, the research aims to provide a method that better captures the specific fat distribution patterns and characteristics of this demographic.
+
+***Implications for Practical Applications***
+
+@potter findings show that while the abdominal circumference method is useful for broad categorization and operational use, it is less effective for individual assessments where greater precision is required.
+This study builds on that foundation by proposing a refined model that combines multiple variables to improve accuracy.
+This approach can be applied in both military and civilian settings where body fat estimation needs to be quick, low-cost, and reliable.
+
+## Simulated Survey
+
+To collect data on body fat estimation using circumference measurements, a well-structured survey was designed to gather relevant information from adult participants.
+The survey starts with an introductory section explaining the purpose of the study, which is to create affordable and practical methods for estimating body fat.
+It assures participants that their data will be kept confidential and used only for research.
+The introduction also provides contact details for the lead researcher in case participants have questions.
+
+The survey is divided into three sections.
+The first section gathers basic demographic details, such as age, gender, and height, to set the context for analysis.
+These straightforward questions help respondents begin the survey with ease.
+The second section focuses on circumference measurements, including wrist and abdomen size, measured in centimeters.
+To ensure consistency, this section includes clear instructions and visual aids, such as diagrams, to guide participants.
+Responses are collected using dropdown fields for precise numerical entries.
+The final section includes optional open-ended questions about participants' general health habits, such as diet and physical activity, to provide additional context about their body composition.
+The survey ends with a thank-you note, acknowledging the participants’ time and effort.
+
+A stratified random sampling method was used to ensure the study represents adults from different age groups and body types, which is important for building a reliable predictive model.
+The target population included adults aged 20 to 70 years.
+Participants were grouped into age brackets (e.g., 20–30, 31–40) to ensure fair representation.
+The sampling frame was built using contacts from community health organizations, fitness centers, and social media recruitment.
+A pilot test with 30 participants helped identify unclear questions and improve measurement instructions.
+
+This methodology uses best practices in survey design by including a mix of question types (e.g., multiple-choice, numerical entries, and open-ended responses) and clear instructions to ensure accurate and consistent data collection.
+By aligning the survey with the study’s goals, the collected data will support the development of effective regression models for estimating body fat.
+The sampling strategy minimizes bias and enhances the ability to apply the findings broadly.
+
+Link to survey: https://forms.gle/353vGHrE5QcBRGuH7
 

### 2024-12-01 scripts/06-model_data.R

@@ -19,4 +19,4 @@ final_model <- lm( as.formula(paste("Pct.BF ~",
 summary(final_model)
 
 #### Save model ####
-saveRDS(final_model, file = "data/03-model_data/final_model.rds")
+saveRDS(final_model, file = "other/model/final_model.rds")

### 2024-12-01 other/datasheet/datadictionary.qmd
updated datasheet & created data dictionary

---
title: "Data Dictionary for Body Fat Dataset"
author: 
  - Wendy Yuan
thanks: "Code and data are available at: https://github.com/kiwindyy/Body-Fat"
date: November 29, 2024
date-format: long
format: pdf
---
**Density**

- Type: Numeric
- Description: Measure of body density, calculated using weight and volume to estimate body fat percentage.
- Values/Range: ~0.99–1.1
- Units: g/cm³
- Remarks: Key variable used to derive body fat percentage.

**Pct.BF**

- Type: Numeric
- Description: Body fat percentage estimated from body density.
- Values/Range: 0–47.5
- Units: Percentage (%)
- Remarks: Outcome variable. Reflects overall fat composition.

**Age**

- Type: Numeric
- Description: Age of the individual in years.
- Values/Range: 20–81
- Units: Years
- Remarks: Reflects life stage, which influences body composition.

**Weight**

- Type: Numeric
- Description: Total body mass in pounds.
- Values/Range: 118.5–262.75
- Units: Pounds (lbs)
- Remarks: Reflects combined weight of bones, muscles, fat, and other tissues.

**Height**

- Type: Numeric
- Description: Standing height of the individual.
- Values/Range: 64–77.75
- Units: Inches
- Remarks: Used with weight for proportions like BMI.

**Neck**

- Type: Numeric
- Description: Circumference of the neck.
- Values/Range: 31.1–43.9
- Units: Centimeters (cm)
- Remarks: Highlights fat and muscle distribution in the upper body.

**Chest**

- Type: Numeric
- Description: Circumference of the chest.
- Values/Range: 79.3–128.3
- Units: Centimeters (cm)
- Remarks: Reflects size and structure of the upper torso, including fat and muscle.

**Abdomen**

- Type: Numeric
- Description: Circumference around the abdomen.
- Values/Range: 69.4–126.2
- Units: Centimeters (cm)
- Remarks: Strongest predictor of body fat percentage, indicates central fat.

**Waist**

- Type: Numeric
- Description: Measurement around the waist.
- Values/Range: 27.3–49.6
- Units: Centimeters (cm)
- Remarks: Assesses fat distribution, often paired with hip circumference.

**Hip**

- Type: Numeric
- Description: Circumference of the hips.
- Values/Range: 85.0–125.6
- Units: Centimeters (cm)
- Remarks: Indicates lower-body proportions, often paired with waist for ratios.

**Thigh**

- Type: Numeric
- Description: Circumference of the thigh.
- Values/Range: 47.2–74.4
- Units: Centimeters (cm)
- Remarks: Highlights fat and muscle distribution in the upper leg.

**Knee**

- Type: Numeric
- Description: Circumference of the knee.
- Values/Range: 33.5–46.0
- Units: Centimeters (cm)
- Remarks: Provides detail about lower-body structure and proportions.

**Ankle**

- Type: Numeric
- Description: Circumference around the ankle.
- Values/Range: 20.2–27.0
- Units: Centimeters (cm)
- Remarks: Reflects skeletal and soft tissue composition in the lower leg.

**Bicep**

- Type: Numeric
- Description: Circumference of the bicep (arm flexed).
- Values/Range: 25.6–39.1
- Units: Centimeters (cm)
- Remarks: Highlights upper-arm muscle and fat distribution.

**Forearm**

- Type: Numeric
- Description: Circumference of the forearm.
- Values/Range: 24.6–33.8
- Units: Centimeters (cm)
- Remarks: Provides information about lower-arm composition.

**Wrist**

- Type: Numeric
- Description: Circumference of the wrist.
- Values/Range: 15.8–21.4
- Units: Centimeters (cm)
- Remarks: Proxy for skeletal size and overall body frame.

### 2024-12-01 other/datasheet/datasheet.qmd
updated datasheet & created data dictionary

@@
 ---
-title: "Datasheet for 'Body Fat Percentage Dataset'"
-subtitle: "My subtitle if needed"
+title: "Datasheet for Body Fat Dataset"
+subtitle: "Predictive Modeling of Body Fat Percentage Using Body Measurements"
 author: 
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This datasheet describes the Body Fat Dataset from Brigham Young University.
+It includes measurements like weight, height, and body circumferences from 250 men.
+The data helps predict body fat percentage using simple methods instead of expensive equipment.
+It is publicly available but only represents men and lacks diversity."
 format: pdf
 number-sections: true
-# bibliography: references.bib
+bibliography: references.bib
 ---
@@
 1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
-    - The dataset was created to enable analysis of Australian politicians.
-We were unable to find a publicly available dataset in a structured format that had the biographical and political information on Australian politicians that was needed for modelling.
+    - This dataset was created to analyze body composition and predict body fat percentage using simpler, more accessible measurements.
+Accurate %body fat measurement can be complex and costly, so this dataset helps in creating prediction models using other physical measurements.
 2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
-    - TBD
+    - Developed by Brigham Young University's (BYU) Human Performance Research Center under the direction of Mark Ricard.
 3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
-    - TBD
+    - BYU Human Performance Research Center, details available at: [https://www.byu.edu/chhp/intro.html#lrc](https://www.byu.edu/chhp/intro.html#lrc)
 4. *Any other comments?*
-    - TBD
+    - The dataset is relevant for health, fitness, and statistical research.
 
@@
 Please provide a description.*
-	- TBD
+	- Each instance represents measurements of a male participant, including body density, body fat percentage, weight, height, and various circumferences (e.g., neck, chest, abdomen).
 2. *How many instances are there in total (of each type, if appropriate)?*
-	- TBD
+	- 250 male participants.
 3.
@@
 If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
-	- TBD
+	- The dataset is a controlled sample of men of various ages. It is not randomized or geographically diverse.
 4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
-	- TBD
+	- Raw numerical data, including weight (in pounds), height (in inches), and circumferences (in inches).
+	- Body fat percentage, a value derived from body density.
 5. *Is there a label or target associated with each instance? If so, please provide a description.*
-	- TBD
+	- Percentage Body Fat (%BF), accurately measured using specialized equipment.
 6.
@@
 This does not include intentionally removed information, but might include, for example, redacted text.*
-	- TBD
+	- No missing data is evident in the dataset.
 7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
-	- TBD
+	- Variables like weight, abdomen circumference, and height have measurable connections with %body fat.
 8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
-	- TBD
+	- The dataset does not come with predefined splits, leaving users the flexibility to create their own training, validation, and test sets.
 9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
-	- TBD
+	- Minor variations in measurements may exist but are not documented.
 10.
@@
 Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
-	- TBD
+	- The dataset is self-contained and can be accessed directly via DASL [@dasl]
 11.
@@
 If so, please provide a description.*
-	- TBD
+	- The dataset is anonymized, containing no personally identifiable information.
 12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
-	- TBD
+	- None.
 13.
@@
 If so, please describe how.*
-	- TBD
+	- The dataset represents males, with no explicit data on race, ethnicity, or geographic distribution.
 15.
@@
 If so, please provide a description.*
-	- TBD
+	- Not possible.
 16. *Any other comments?*
-	- TBD
+	- Contains health-related data (e.g., %body fat) but no personal or private data.
 
@@
 If so, please describe how.*
-	- TBD
+	- Measurements were collected through standard anthropometric techniques, supplemented with accurate %body fat calculations based on body density.
 2.
@@
 How were these mechanisms or procedures validated?*
-	- TBD
+	- Likely involved common health assessment tools and equipment.
 3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
-	- TBD
+	- A non-random, controlled sample of male participants from BYU’s study pool.
 4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
-	- TBD
+	- Researchers at BYU Human Performance Research Center.
 5.
@@
 If not, please describe the timeframe in which the data associated with the instances was created.*
-	- TBD
+	- Unspecified but likely during a single study period.
 6.
@@
 If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
-	- TBD
+	- Ethical review details are not provided.
 7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
-	- TBD
+	- Data was collected directly from study participants.
 8.
@@
 If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
-	- TBD
+	- Likely obtained as part of the study; details not included.
 9.
@@
 If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
-	- TBD
+	- Not explicitly mentioned.
 10.
@@
 If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
-	- TBD
+	- Not explicitly mentioned.
 11.
@@
 If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
-	- TBD
-12. *Any other comments?*
-	- TBD
+	- None conducted or documented.
 
@@
 If not, you may skip the remaining questions in this section.*
-	- TBD
+	- No significant preprocessing; raw data is presented for analysis.
 2.
@@
 If so, please provide a link or other access point to the "raw" data.*
-	- TBD
+	- Provided in its entirety.
 3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
-	- TBD
-4. *Any other comments?*
-	- TBD
+	- DataDesk integration for visualization and analysis.
 
@@
 1. *Has the dataset been used for any tasks already? If so, please provide a description.*
-	- TBD
+	- Statistical modeling of body fat percentage.
+	- Regression modeling and variable selection analysis.
 2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
-	- TBD
+	- [https://github.com/kiwindyy/Body-Fat](https://github.com/kiwindyy/Body-Fat)
 3. *What (other) tasks could the dataset be used for?*
-	- TBD
+	- Machine learning for health and fitness prediction.
+	- Biostatistical research and educational tools.
 4.
@@
 Is there anything a dataset consumer could do to mitigate these risks or harms?*
-	- TBD
+	- Dataset is limited to male participants.
+	- Results cannot be generalized to the entire population without validation.
 5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
-	- TBD
-6. *Any other comments?*
-	- TBD
+	- Misuse for discriminatory purposes.
+	Use in contexts that promote harmful body image stereotypes.
 
@@
 If so, please provide a description.*
-	- TBD
+	- Available via DASL [@dasl] and DataDesk integration.
 2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
-	- TBD
+	- Downloadable from DASL in .txt format.
 3. *When will the dataset be distributed?*
-	- TBD
+	- It is a public dataset
 4.
@@
 If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
-	- TBD
+	- No explicit restrictions noted.
 5.
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
-	- TBD
+	- None mentioned.
 6.
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
-	- TBD
-7. *Any other comments?*
-	- TBD
+	- Not applicable.
 
@@
 1. *Who will be supporting/hosting/maintaining the dataset?*
-	- TBD
+	- Maintained by DASL [@dasl] and BYU Human Performance Research Center.
 2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
-	- TBD
+	- Director: Mark Ricard
+	- Contact: (801) 378-8958
 3. *Is there an erratum? If so, please provide a link or other access point.*
-	- TBD
+	- None documented.
 4.
@@
 If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
-	- TBD
+	- Dataset is static, with no planned updates.
 5.
@@
 If so, please describe these limits and explain how they will be enforced.*
-	- TBD
+	- Retained indefinitely for public use.
 6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
-	- TBD
+	- Only the current version is available.
 7.
@@
 If so, please provide a description.*
-	- TBD
-8. *Any other comments?*
-	- TBD
+	- Contributions or augmentation not supported.
 

### 2024-12-01 paper/paper.qmd
updated datasheet & created data dictionary

@@
 - Weight: The total body mass of the individual, reflecting the combined weight of bones, muscles, fat, and other tissues.
-- Height: The standing height of the individual, often used alongside weight to calculate proportions and indices like BMI.
+- Height: The standing height of the individual, often used alongside weight to calculate proportions and indices.
 - Neck: The circumference of the neck, offering a measurement of fat and muscle distribution in the upper body.
@@
 
-Link to survey: https://forms.gle/353vGHrE5QcBRGuH7
+Link to survey: [https://forms.gle/353vGHrE5QcBRGuH7](https://forms.gle/353vGHrE5QcBRGuH7)
 

### 2024-12-02 other/datasheet/datadictionary.qmd
cleaned r code

@@
 ---
-title: "Data Dictionary for Body Fat Dataset"
+title: "Data Dictionary for Body Fat Raw Dataset"
 author: 
@@
 - Description: Age of the individual in years.
-- Values/Range: 20–81
+- Values/Range: 22–81
 - Units: Years
@@
 - Values/Range: 27.3–49.6
-- Units: Centimeters (cm)
+- Units: Inches (in)
 - Remarks: Assesses fat distribution, often paired with hip circumference.
@@
 - Description: Circumference of the knee.
-- Values/Range: 33.5–46.0
+- Values/Range: 33.0–46.0
 - Units: Centimeters (cm)
@@
 - Description: Circumference around the ankle.
-- Values/Range: 20.2–27.0
+- Values/Range: 19.1–33.9
 - Units: Centimeters (cm)
@@
 - Description: Circumference of the bicep (arm flexed).
-- Values/Range: 25.6–39.1
+- Values/Range: 24.8–39.1
 - Units: Centimeters (cm)
@@
 - Description: Circumference of the forearm.
-- Values/Range: 24.6–33.8
+- Values/Range: 21.0–34.9
 - Units: Centimeters (cm)

### 2024-12-02 scripts/00-simulate_data.R

@@ -1,16 +1,15 @@
 #### Preamble ####
 # Purpose: Simulates the body fat data
-  #Abdomen, Wrist, Weight
 # Author: Wendy Yuan
 # Date: 29 November 2024
-# Contact: w.yuan@mail.utoronto.ca 
+# Contact: w.yuan@mail.utoronto.ca
 
 #### Workspace setup ####
 library(tidyverse)
 set.seed(1009122423)
 
 #### Simulate Data ####
-# Mean and SD values are from the National Health and Nutrition Examination 
+# Mean and SD values are from the National Health and Nutrition Examination
 # Survey and Anthropometric Data for U.S. Adults
 
 #variable, Mean(Approx.), Standard Deviation (Approx.)
@@ -58,28 +57,28 @@ repeat {
     Wrist = rnorm(n, mean = 18, sd = 2)
   )
   
-  if (all(simulated_data >0)) {
+  if (all(simulated_data > 0)) {
     break
   }
 }
 
 # Truncate simulated values to the same number of digits of the original
-simulated_data$Density = round(simulated_data$Density, digits = 4)
-simulated_data$Pct.BF = round(simulated_data$Pct.BF, digits = 1)
-simulated_data$Age = round(simulated_data$Age, digits = 0)
-simulated_data$Weight = round(simulated_data$Weight, digits = 2)
-simulated_data$Height = round(simulated_data$Height, digits = 2)
-simulated_data$Neck = round(simulated_data$Neck, digits = 1)
-simulated_data$Chest = round(simulated_data$Chest, digits = 1)
-simulated_data$Abdomen = round(simulated_data$Abdomen, digits = 1)
-simulated_data$Waist = round(simulated_data$Waist, digits = 5)
-simulated_data$Hip = round(simulated_data$Hip, digits = 1)
-simulated_data$Thigh = round(simulated_data$Thigh, digits = 1)
-simulated_data$Knee = round(simulated_data$Knee, digits = 1)
-simulated_data$Ankle = round(simulated_data$Ankle, digits = 1)
-simulated_data$Bicep = round(simulated_data$Bicep, digits = 1)
-simulated_data$Forearm = round(simulated_data$Forearm, digits = 1)
-simulated_data$Wrist = round(simulated_data$Wrist, digits = 1)
+simulated_data$Density <- round(simulated_data$Density, digits = 4)
+simulated_data$Pct.BF <- round(simulated_data$Pct.BF, digits = 1)
[…]

### 2024-12-02 scripts/01-test_simulated_data.R

@@ -2,9 +2,9 @@
 # Purpose: Tests the structure and validity of the simulated body fat dataset
 # Author: Wendy Yuan
 # Date: 29 November 2024
-# Contact: w.yuan@mail.utoronto.ca 
-# Pre-requisites: 
-  # - 00-simulate_data.R must have been run
+# Contact: w.yuan@mail.utoronto.ca
+# Pre-requisites:
+# - 00-simulate_data.R must have been run
 
 #### Workspace setup ####
 library(tidyverse)
@@ -70,12 +70,13 @@ if (all(sim_data$Density >= 0.9 & sim_data$Density <= 1.1)) {
 }
 
 # Test if all values in body measurement columns are positive
-non_positive_cols <- names(sim_data)[sapply(sim_data, function(column) 
-  any(column <= 0))]
-if (length(non_positive_cols) == 0 ) {
+non_positive_cols <- names(sim_data)[sapply(sim_data, function(column) {
+  any(column <= 0)
+})]
+if (length(non_positive_cols) == 0) {
   message("Test Passed: All body measurements are positive.")
 } else {
-  stop(paste("Test Failed: Some values in '", paste(non_positive_cols, 
+  stop(paste("Test Failed: Some values in '", paste(non_positive_cols,
                                                     collapse = ", "),
              "' column(s) are not positive."))
 }

### 2024-12-02 scripts/02-download_data.R

@@ -2,7 +2,7 @@
 # Purpose: Downloads and saves the data from DASL
 # Author: Wendy Yuan
 # Date: 29 November 2024
-# Contact: w.yuan@mail.utoronto.ca 
+# Contact: w.yuan@mail.utoronto.ca
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-12-02 scripts/03-clean_data.R

@@ -2,7 +2,7 @@
 # Purpose: Downloads and saves the data from DASL
 # Author: Wendy Yuan
 # Date: 29 November 2024
-# Contact: w.yuan@mail.utoronto.ca 
+# Contact: w.yuan@mail.utoronto.ca
 
 #### Workspace setup ####
 library(tidyverse)
@@ -21,18 +21,18 @@ cleaned_data <- data %>% drop_na()
 cleaned_data <- cleaned_data %>% distinct()
 
 # define percentile curoff
-lower_cutoff = 0.25
-upper_cutoff = 0.75
+lower_cutoff <- 0.25
+upper_cutoff <- 0.75
 
 # Function to remove outlines, ensure all values are greater than 0
-epsilon = 1e-10
+epsilon <- 1e-10
 remove_outliers <- function(data, column) {
-  Q1 <- quantile(data[[column]], lower_cutoff, na.rm = TRUE)
-  Q3 <- quantile(data[[column]], upper_cutoff, na.rm = TRUE)
-  IQR <- Q3 - Q1
-  lower_bound <- max(Q1 - 1.5 * IQR, epsilon)
+  q1 <- quantile(data[[column]], lower_cutoff, na.rm = TRUE)
+  q3 <- quantile(data[[column]], upper_cutoff, na.rm = TRUE)
+  iqr <- q3 - q1
+  lower_bound <- max(q1 - 1.5 * iqr, epsilon)
   message(paste(column, ":", lower_bound))
-  upper_bound <- Q3 + 1.5 * IQR
+  upper_bound <- q3 + 1.5 * iqr
   
   data %>% filter(data[[column]] >= lower_bound & data[[column]] <= upper_bound)
 }
@@ -45,8 +45,8 @@ for (column_name in colnames(cleaned_data)) {
   }
 }
 
-# The original dataset includes weight in pounds, height and waist in inches, 
-# and body fat in g/m³. The remaining measurements are in centimeters. 
+# The original dataset includes weight in pounds, height and waist in inches,
+# and body fat in g/m³. The remaining measurements are in centimeters.
 # Normalize the units for the following columns:
 
 #lbs to kg (Keep two decimal places)
@@ -57,7 +57,7 @@ cleaned_data$Weight <- floor(cleaned_data$Weight * 100) / 100
 cleaned_data$Height <- cleaned_data$Height * 2.54
[…]

### 2024-12-02 scripts/04-test_analysis_data.R

@@ -3,7 +3,7 @@
 # Author: Wendy Yuan
 # Date: 29 November 2024
 # Contact: w.yuan@mail.utoronto.ca
-# Pre-requisites: 
+# Pre-requisites:
 # - 02-clean_data.R must have been run
 
 #### Workspace setup ####
@@ -12,9 +12,8 @@ library(testthat)
 library(arrow)
 library(dplyr)
 
-# Load the cleaned dataset, the test starts in scripts folder, use relative 
-# path to find data folder.
-cleaned_data <- read_parquet(here::here("data/02-analysis_data/bodyfat.parquet"))
+cleaned_data <- read_parquet(here::here("data/02-analysis_data/bodyfat.parquet")
+)
 
 #### Test cleaned data ####
 

### 2024-12-02 scripts/05-exploratory_data_analysis.R

@@ -2,8 +2,8 @@
 # Purpose: Exploratory data analysis on variables
 # Author: Wendy Yuan
 # Date: 29 November 2024
-# Contact: w.yuan@mail.utoronto.ca 
-# Pre-requisites: 
+# Contact: w.yuan@mail.utoronto.ca
+# Pre-requisites:
 # - 03-clean_data.R must have been run
 
 
@@ -15,7 +15,7 @@ library(knitr)
 
 #### Read data ####
 data <- read_parquet("data/02-analysis_data/bodyfat.parquet")
-data <- data[ , !(names(data) %in% c("Density"))]
+data <- data[, !(names(data) %in% c("Density"))]
 
 # Full model using all variables except Density
 full_model <- lm(Pct.BF ~ ., data = data)
@@ -26,14 +26,17 @@ backward_model <- stepAIC(full_model, direction = "backward", trace = 0)
 # Extract the final 4-variable model
 final_variables <- names(coef(backward_model))[-1] # Exclude intercept
 while (length(final_variables) > 4) {
-  current_model <- lm(as.formula(paste("Pct.BF ~",
-                          paste(final_variables, collapse = "+"))), data = data)
+  current_model <- lm(as.formula(paste("Pct.BF ~", paste(final_variables,
+                                                         collapse = "+"))),
+                      data = data)
   current_aic <- AIC(current_model)
   
   # Drop one variable at a time and calculate AIC
   aic_values <- sapply(final_variables, function(var) {
-    temp_model <- lm(as.formula(paste("Pct.BF ~", paste(setdiff(
-      final_variables, var), collapse = "+"))), data = data)
+    temp_model <- lm(as.formula(paste("Pct.BF ~", paste(setdiff(final_variables,
+                                                                var),
+                                                        collapse = "+"))),
+                     data = data)
     return(AIC(temp_model))
   })
   

### 2024-12-02 scripts/06-model_data.R

@@ -2,20 +2,21 @@
 # Purpose: Build final model
 # Author: Wendy Yuan
 # Date: 29 November 2024
-# Contact: w.yuan@mail.utoronto.ca 
-# Pre-requisites: 
+# Contact: w.yuan@mail.utoronto.ca
+# Pre-requisites:
 # - 05-exploratory-data_analysis.R must have been run
 
 library(arrow)
 
 # Final variables learned from 05-exploratory-data_analysis.R
-final_variables <- c( "Age", "Height", "Abdomen", "Wrist" )
+final_variables <- c("Age", "Height", "Abdomen", "Wrist")
 
-data <- read_parquet( "data/02-analysis_data/bodyfat.parquet" )
+data <- read_parquet("data/02-analysis_data/bodyfat.parquet")
 
 # Final 4-variable model
-final_model <- lm( as.formula(paste("Pct.BF ~", 
-                        paste(final_variables, collapse = "+"))), data = data )
+final_model <- lm(as.formula(paste("Pct.BF ~", paste(final_variables,
+                                                     collapse = "+"))),
+                  data = data)
 summary(final_model)
 
 #### Save model ####

### 2024-12-02 paper/paper.qmd
further explained some aspects of the data

@@
 ---
-title: "Estimating Body Fat Using Circumference Measurements"
+title: "Estimating Body Fat Percentage"
 subtitle: "Abdomen as the Strongest Predictor With Contributions From Wrist, Height, and Age For Affordable Health Monitoring"
@@
 Current methods, like DXA scans and underwater weighing, are very reliable but often expensive, difficult to access, or only available in specialized facilities.
-More affordable methods, like using a measuring tape for body size, can provide reasonable estimates of body fat and are easier for more people to use [@measurement].
+More affordable methods, like body circumference measuring, can provide reasonable estimates of body fat [@measurement].
 A lack of easy and reliable ways to measure body fat can lead to missed chances to detect health risks.
@@
 @sec-discussion interprets the findings, notes limitations, and suggests improvements.
-@sec-a is the raw dataset before any cleaning.
-@sec-b explores survey, sampling, and observational data methods, including measurement techniques, simulations.
+@sec-raw & @sec-regassumption & @sec-aic contain supporting data information.
+@sec-survey explores survey, sampling, and observational data methods, including measurement techniques, simulations.
 
@@
 This study uses the statistical programming language R [@citeR] and the packages: tidyverse  [@tidyverse], Arrow [@arrow], MASS [@mass], GGally [@ggally], gridExtra [@gridextra], Knitr [@knitr], kableExtra [@kableextra], Car [@car], TestThat [@testthat], dplyr [@dplyr], readr [@readr], tidyr [@tidyr].
+The data used in this study is obtained from The Data And Story Library [@dasl].
 
@@
 Before analysis, the raw dataset was cleaned to standardize and prepare the data for use.
-Since the original dataset included measurements in both inches and centimeters, all measurements were converted into centimeters to ensure uniformity, as detailed in [@tbl-cleaned1] & [@tbl-cleaned2].
+Since the original dataset included measurements in both inches and centimeters, all measurements were converted into centimeters to ensure uniformity.
+Additionally, measurements in pounds were converted to kilograms.
+[@tbl-cleaned1] & [@tbl-cleaned2] & [@tbl-cleaned3] show the first 8 observations of the cleaned data.
 Additional cleaning steps included removing duplicates, addressing outliers, and removing missing observations to improve dataset’s usability.
 This cleaned data makes sure that the variables in the study are accurate and consistent.
-For reference, the original dataset before cleaning is provided in [@tbl-raw1] & [@tbl-raw2] in @sec-a, showing the changes made during this process.
+For reference, the original dataset before cleaning (first 10 observation) is provided in [@tbl-raw1] & [@tbl-raw2] in @sec-raw, showing the changes made during this process.
 
@@
 # Split into two smaller tables
-part1 <- data[, 1:8]  # First 8 columns
-part2 <- data[, 9:16]  # Remaining 8 columns
+part1 <- data[, 1:5]  # First 5 columns
+part2 <- data[, 6:10]  # Next 5 columns
+part3 <- data[, 11:16]  # Remaining 6 columns
+
+# Update column names to include units
+colnames(part1) <- c(
+  "Density (g/cm³)", "Pct.BF (%)", "Age (years)", "Weight (kg)", "Height (cm)")
 
 # Render each part
-kable(head(part1, 10), booktabs = TRUE) %>%
+kable(head(part1, 8), booktabs = TRUE) %>%
   kable_styling(latex_options = c("hold_position", "scale_down"))
@@
 
-kable(head(part2, 10), booktabs = TRUE) %>%
+colnames(part2) <- c(
+  "Neck (cm)", "Chest (cm)", "Abdomen (cm)", "Waist (cm)", "Hip (cm)")
+
+kable(head(part2, 8), booktabs = TRUE) %>%
+  kable_styling(latex_options = c("hold_position", "scale_down"))
+```
+
+```{r}
+#| label: tbl-cleaned3
+#| tbl-cap: Cleaned Data of Body Fat Variables Part 3
+#| echo: false
+#| warning: false
+#| message: false
+
+colnames(part3) <- c(
+  "Thigh (cm)", "Knee (cm)", "Ankle (cm)",
+  "Bicep (cm)", "Forearm (cm)", "Wrist (cm)")
+
+kable(head(part3, 8), booktabs = TRUE) %>%
   kable_styling(latex_options = c("hold_position", "scale_down"))
@@
 
+Body fat percent is measured in percentage (%).
+Using the method from ...
+body fat percentage is calculated using the relationship between body density ($D$) and the densities of lean and fat tissue.
+The formula for the proportion of fat tissue ($B$) is:
+
+$$B = \frac{1}{D} \cdot \frac{ab}{a - b} - \frac{b}{a - b}$$
+
+For example: If $a=1.10g/cm^3$ (lean tissue density), $b=0.90g/cm^3$ (fat tissue density), and $D=1.0708g/cm^3$. Once $B$ is found, percent body fat (pct.BF) is calculated as:
+
+$$\text{PctBF} = 100 \cdot B$$
+
+The calculation gives about 12.27% body fat. This method provides a simple way to estimate body fat for regression analysis.
+
 As shown in [@fig-pctbf], the histogram of percent body fat has a shape that is close to bell-like, though it is not perfectly symmetrical.
+The values range between 0 to 47.5.
 Most individuals in the dataset have body fat levels clustered within a common range, with fewer individuals having much higher or much lower levels.
@@
 #| label: fig-pctbf
-#| fig-cap: Distribution of Percent Body Fat
+#| fig-cap: Histogram Distribution of Percent Body Fat
 #| echo: false
@@
 
+\newpage
+
 ## Predictor variables
@@
 
-- Density: The measure of body density, used as a key variable in estimating body fat percentage. It combines body weight and volume to provide insights into overall composition.
-- Age: The age of the individual in years, providing a measure of the person's stage of life, which can influence body composition.
-- Weight: The total body mass of the individual, reflecting the combined weight of bones, muscles, fat, and other tissues.
-- Height: The standing height of the individual, often used alongside weight to calculate proportions and indices.
-- Neck: The circumference of the neck, offering a measurement of fat and muscle distribution in the upper body.
-- Chest: The circumference of the chest, reflecting the size and structure of the upper torso, including muscle and fat.
+- Density: The measure of body density, used as a key variable in estimating body fat percentage.
+It combines body weight and volume to provide insights into overall composition.
+It is measured in grams per $cm^3$ with values ranging from 0.99 to 1.1.
+- Age: The age of the individual in years, providing a measure of the person's stage of life, which can influence body composition. It is measured in years with values ranging from 20 to 81.
+- Weight: The total body mass of the individual, reflecting the combined weight of bones, muscles, fat, and other tissues. It is measured in pounds (lbs) with values ranging from 118.5-262.75.
+- Height: The standing height of the individual, often used alongside weight to calculate proportions and indices. It is measured in inches (in) with values ranging from 64–77.75.
+- Neck: The circumference of the neck, offering a measurement of fat and muscle distribution in the upper body. It is measured in centimeters (cm) with values ranging from 31.1-43.9.
+- Chest: The circumference of the chest, reflecting the size and structure of the upper torso, including muscle and fat. It is measured in centimeters (cm) with values ranging from 79.3-128.3.
 - Abdomen: The circumference around the abdomen, a key indicator of central fat distribution and a significant predictor of body fat percentage.
-- Waist: The measurement around the waist, often used with hip circumference to assess body shape and fat distribution.
+It is measured in centimeters (cm) with values ranging from 69.4-126.2.
+- Waist: The measurement around the waist, often used with hip circumference to assess body shape and fat distribution. It is measured in centimeters (cm) with values ranging from 27.3-49.6.
 - Hip: The circumference of the hips, providing a measure of lower-body proportions and often paired with waist circumference to calculate ratios.
-- Thigh: The circumference of the thigh, measured to understand muscle and fat distribution in the upper leg.
-- Knee: The circumference of the knee, offering additional detail about lower-body structure and proportions.
-- Ankle: The measurement around the ankle, reflecting skeletal and soft tissue composition in the lower leg.
-- Bicep: The circumference of the bicep, measured with the arm flexed, highlighting upper-arm muscle and fat distribution.
-- Forearm: The circumference of the forearm, providing information about the composition of the lower arm.
-- Wrist: The circumference of the wrist, a useful proxy for skeletal size and overall body frame.
+It is measured in centimeters (cm) with values ranging from 85.0-125.6.
+- Thigh: The circumference of the thigh, measured to understand muscle and fat distribution in the upper leg. It is measured in centimeters (cm) with values ranging from 47.2-74.4.
+- Knee: The circumference of the knee, offering additional detail about lower-body structure and proportions. It is measured in centimeters (cm) with values ranging from 33.5-46.0.
+- Ankle: The measurement around the ankle, reflecting skeletal and soft tissue composition in the lower leg. It is measured in centimeters (cm) with values ranging from 20.2-27.0.
+- Bicep: The circumference of the bicep, measured with the arm flexed, highlighting upper-arm muscle and fat distribution. It is measured in centimeters (cm) with values ranging from 25.6-39.1.
+- Forearm: The circumference of the forearm, providing information about the composition of the lower arm. It is measured in centimeters (cm) with values ranging from 24.6-33.8.
+- Wrist: The circumference of the wrist, a useful proxy for skeletal size and overall body frame. It is measured in centimeters (cm) with values ranging from 15.8-21.4.
 
-To focus on the most important variables, this study used backward selection to find the four that gave the best model fit, with the lowest Akaike Information Criterion (AIC).
-Backward selection works by starting with all the variables and gradually removing those that add the least to explaining body fat percentage, based on statistical rules.
-This process ensures the final set of variables is strongly related to the outcome.
-As shown in [@fig-aic], this approach narrowed the variables down to Age, Height, Abdomen, and Wrist circumference.
-These four were chosen because they worked together to provide the best explanation of the differences in body fat levels while keeping the model simple and effective.
+This study focuses on only four variables.
+To find the most important ones, backward selection was used to identify the four variables that provided the best model fit, measured by the lowest Akaike Information Criterion (AIC).
+For this method to work, all variables needed to meet the linear regression assumptions.
+As discussed in @sec-regassumption, the analysis showed that all 15 variables meet these assumptions when tested against body fat percentage (Pct.BF).
+With these conditions met, the study proceeds using AIC to keep the model simple while still explaining the data well.
+
+Backward selection starts with all the variables and gradually removes those that contribute the least to predicting body fat percentage, based on AIC.
+The process begins with a full model using all variables (excluding Density, as it is directly used to calculate body fat percentage) and continues until only four variables remain.
+The four variables selected are: **Age, Height, Abdomen, and Wrist**, as seen in @fig-aic.
+They were chosen because they explain differences in body fat percentage well while keeping the model easy to interpret.
+For a more detailed explanation of this process, see @sec-aic or the script documented in scripts/05-exploratory_data_analysis.R.
 
@@
 
+\newpage
+
 The histograms of Age, Height, Abdomen, and Wrist shown in [@fig-predictor] explain their role in predicting body fat.
@@
 #| label: fig-predictor
-#| fig-cap: Distributions of Age, Height, Abdomen, Wrist
+#| fig-cap: Histogram Distributions of Age, Height, Abdomen, Wrist
 
@@
 The pairwise plot, [@fig-pairwise], shows how Age, Height, Abdomen, and Wrist are related to each other.
-Abdomen and Wrist have the strongest relationship.
+Abdomen and Wrist have the strongest relationship in all the selected variables - as they have a rough linear shape in the pairwise plot.
 Larger abdominal circumferences are generally linked to larger wrists, showing overall body size.
@@
 
-$y_i = \beta_0 + \beta_1 x_{1i} + \beta_2 x_{2i} + \beta_3 x_{3i} + \beta_4 x_{4i}$
+$$y_i = \beta_0 + \beta_1 x_{1i} + \beta_2 x_{2i} + \beta_3 x_{3i} + \beta_4 x_{4i} + \epsilon_i$$
 
@@
 Age has a weak positive effect, meaning body fat percentage may slightly increase with age, but this result is less certain.
+The p-value of each variable tells us the likely the data would have occurred.
+Assuming the alpha significance level is $\alpha$ = 0.05 then height, abdomen & wrist would be good predictors for body fat percentage.
+However, since the p-value of age is 0.08 (greater than 0.05) then it is not necessarily a good predictor for body fat percentage.
 
@@
 ```
+
+\newpage
 
@@
 
-# Raw Data of Body Fat Percentage {#sec-a}
+# Raw Data of Body Fat Percentage {#sec-raw}
 
@@
 
-# Surveys, sampling, and observational data {#sec-b}
+# All Variable Linear Regression Assumption {#sec-regassumption}
+
+The diagnostic plots confirm that the linear regression assumptions are met for all variables, supporting the model's reliability.
+The Residuals vs.
+Fitted plot, @fig-fullresidual, shows that the residuals are randomly scattered around the horizontal red line at zero, with no noticeable patterns or curvature.
+This suggests that the relationship between the predictors and the outcome is properly captured by the linear regression model, satisfying the linearity assumption.
+Additionally, the absence of clustering or systematic trends indicates that the residuals are not related to one another, meeting the independence assumption.
+
+```{r}
+#| label: fig-fullresidual
+#| fig-cap: Residual Plot Verifying the Linearity for All Variables
+#| echo: false
+#| warning: false
+#| message: false
+
+# Fit the linear regression model
+fullresidual <- lm(Pct.BF ~ Age + Weight + Height + Neck + Chest + Abdomen + Waist + 
+              Hip + Thigh + Knee + Ankle + Bicep + Forearm + Wrist, data = data)
+
+# Linearity: Residuals vs Fitted Plot
+plot(fullresidual$fitted.values, residuals(fullresidual), 
+     main = "Residuals vs Fitted",
+     xlab = "Fitted Values",
+     ylab = "Residuals")
+abline(h = 0, col = "red")
+```
+
+The Scale-Location plot, @fig-fullvariance, further supports the model by demonstrating that the residuals are evenly spread across the range of fitted values.
+The residuals do not show a funnel shape or varying spread, and the red trend line remains fairly flat, confirming that the constant variance assumption (homoscedasticity) holds.
+This ensures that the model does not suffer from uneven variability, which could affect the results.
+
+```{r}
+#| label: fig-fullvariance
+#| fig-cap: Scale Location Verifying Constance Variance for All Variables
+#| echo: false
+#| warning: false
+#| message: false
+
+plot(fullresidual, which = 3)
+```
+
+Lastly, the Normal Q-Q plot, @fig-fullnormality, shows that the residuals closely follow the red diagonal line, meaning they are approximately normally distributed.
+While there are minor deviations at the ends, they are not significant enough to impact the model's validity.
+This satisfies the normality assumption, which is necessary for accurate hypothesis testing and confidence intervals in linear regression.
+
+```{r}
+#| label: fig-fullnormality
+#| fig-cap: QQ-Plot Verifying the Normality of Errors for All Variables
+#| echo: false
+#| warning: false
+#| message: false
+
+# Normality: Q-Q Plot of Residuals
+qqnorm(residuals(fullresidual))
+qqline(residuals(fullresidual), col = "red")
+```
+
+Since the assumptions are satisfied, we can confidently move forward with evaluating the model.
+
+# AIC Backwards Selection Explained {#sec-aic}
+
+This script performs backward selection to identify the four variables that best predict body fat percentage (Pct.BF) while minimizing the Akaike Information Criterion (AIC).
+Here's a breakdown of what each part of the code does:
+
+1. Setup and Data Preparation:
+    - The necessary libraries (tidyverse, arrow, MASS, and knitr) are loaded.
+    - The dataset is read from a .parquet file, and the Density variable is excluded because it is directly related to body fat percentage.
+
+2. Full Model Creation:
+    - A linear regression model (full_model) is fit using all variables in the dataset, excluding Density.
+
+3. Initial Backward Selection with stepAIC:
+    - The stepAIC function from the MASS package is used to perform backward selection.
+This function starts with the full model and removes variables one by one, based on AIC, until no further improvement can be made.
+
+4. Refinement to Four Variables:
+    - The code then refines the model further to ensure it includes exactly four variables.
+It starts with the variables identified by stepAIC and iteratively removes the variable that contributes the least to reducing AIC, recalculating AIC after each removal.
+    - This process continues until only four variables remain.
+
+5. Output the Final Variables:
+    - The final four variables selected by the backward selection process are displayed in a table using the kable function.
+
+This process is outlined in reference document scripts/05-exploratory_data_analysis.R. The script automates the selection process, making it systematic and reproducible.
+
+# Surveys, sampling, and observational data {#sec-survey}
 

### 2024-12-03 paper/paper.qmd
updated some formating
made some lintr changes & changes some mistakes

@@
 ---
-title: "Estimating Body Fat Percentage"
+title: "Estimating Body Fat Percentage Using Anthropometric Measurements"
 subtitle: "Abdomen as the Strongest Predictor With Contributions From Wrist, Height, and Age For Affordable Health Monitoring"
@@
 Body fat percent is measured in percentage (%).
-Using the method from ...
-body fat percentage is calculated using the relationship between body density ($D$) and the densities of lean and fat tissue.
+The method and numbers (for the example) are from @katch.
+Body fat percentage is calculated using the relationship between body density ($D$) and the densities of lean and fat tissue.
 The formula for the proportion of fat tissue ($B$) is:
@@
 It is measured in grams per $cm^3$ with values ranging from 0.99 to 1.1.
-- Age: The age of the individual in years, providing a measure of the person's stage of life, which can influence body composition. It is measured in years with values ranging from 20 to 81.
+- Age: The age of the individual in years, providing a measure of the person's stage of life, which can influence body composition. It is measured in years with values ranging from 22 to 81.
 - Weight: The total body mass of the individual, reflecting the combined weight of bones, muscles, fat, and other tissues. It is measured in pounds (lbs) with values ranging from 118.5-262.75.
@@
 It is measured in centimeters (cm) with values ranging from 69.4-126.2.
-- Waist: The measurement around the waist, often used with hip circumference to assess body shape and fat distribution. It is measured in centimeters (cm) with values ranging from 27.3-49.6.
+- Waist: The measurement around the waist, often used with hip circumference to assess body shape and fat distribution. It is measured in inches (in) with values ranging from 27.3-49.6.
 - Hip: The circumference of the hips, providing a measure of lower-body proportions and often paired with waist circumference to calculate ratios.
@@
 - Thigh: The circumference of the thigh, measured to understand muscle and fat distribution in the upper leg. It is measured in centimeters (cm) with values ranging from 47.2-74.4.
-- Knee: The circumference of the knee, offering additional detail about lower-body structure and proportions. It is measured in centimeters (cm) with values ranging from 33.5-46.0.
-- Ankle: The measurement around the ankle, reflecting skeletal and soft tissue composition in the lower leg. It is measured in centimeters (cm) with values ranging from 20.2-27.0.
+- Knee: The circumference of the knee, offering additional detail about lower-body structure and proportions. It is measured in centimeters (cm) with values ranging from 33.0-46.0.
+- Ankle: The measurement around the ankle, reflecting skeletal and soft tissue composition in the lower leg. It is measured in centimeters (cm) with values ranging from 19.1–33.9.
 - Bicep: The circumference of the bicep, measured with the arm flexed, highlighting upper-arm muscle and fat distribution. It is measured in centimeters (cm) with values ranging from 25.6-39.1.
-- Forearm: The circumference of the forearm, providing information about the composition of the lower arm. It is measured in centimeters (cm) with values ranging from 24.6-33.8.
+- Forearm: The circumference of the forearm, providing information about the composition of the lower arm. It is measured in centimeters (cm) with values ranging from 21.0–34.9.
 - Wrist: The circumference of the wrist, a useful proxy for skeletal size and overall body frame. It is measured in centimeters (cm) with values ranging from 15.8-21.4.
@@
 
+par(cex = 0.8)
+
 # 1. Linearity: Residuals vs Fitted Plot
@@
 
+par(cex = 0.8)
+
 plot(model, which = 3)
 ```
+
+\newpage
 
@@
 
+par(cex = 0.8)
+
 # 4. Normality: Q-Q Plot of Residuals
@@
 ```
+
+The multi-linear regression model was chosen for its simplicity, ease of understanding, and ability to show important relationships between measurements while meeting the basic requirements of linear regression, such as consistency and fairness in the results.
+Unlike more complicated methods, such as machine learning or non-linear models, multi-linear regression makes it easier to interpret how each factor affects body fat estimation, making it more useful for practical applications and understandable for non-experts.
+This model connects the findings with existing knowledge by confirming known patterns, such as the strong connection between abdominal size and body fat, which aligns with the idea that fat around the abdomen is a main indicator of overall fat levels.
+Including wrist size and height emphasizes differences in body structure and proportions, adding more detail to how body fat is distributed.
+By combining known ideas with real-world testing, this model provides a practical, clear, and easy way to estimate body fat, especially for everyday use, while building on current understanding.
+
+\newpage
 
@@
 The regression results are summarized in [@tbl-multi1], showing the coefficients and pvalues & [@tbl-multi2], showing the $R^2$ and standard error.
+For the code and full model see the script document in: scripts/06-model_data.R.
 The intercept, which represents the estimated body fat percentage when all predictors are zero, is 2.01.
@@
 A more balanced dataset would also make it easier to detect patterns that apply to specific groups.
-
 Researchers should also consider adding more predictors to the model.
@@
 Future studies could also use data collected over time to see how body fat changes as people age and whether the same predictors still apply.
-This would help create a better understanding of body fat and how it changes throughout life.
+This would help create a better understanding of body fat and how it changes.
 
@@
 
+\newpage
+
 # All Variable Linear Regression Assumption {#sec-regassumption}
@@
 # Fit the linear regression model
-fullresidual <- lm(Pct.BF ~ Age + Weight + Height + Neck + Chest + Abdomen + Waist + 
-              Hip + Thigh + Knee + Ankle + Bicep + Forearm + Wrist, data = data)
+fullresidual <- lm(Pct.BF ~ Age + Weight + Height + Neck + Chest + Abdomen + 
+      Waist + Hip + Thigh + Knee + Ankle + Bicep + Forearm + Wrist, data = data)
+
+par(cex = 0.8)
 
@@
 
+par(cex = 0.8)
+
 plot(fullresidual, which = 3)
@@
 
+par(cex = 0.8)
+
 # Normality: Q-Q Plot of Residuals
@@
 Since the assumptions are satisfied, we can confidently move forward with evaluating the model.
+
+\newpage
 
@@
 
+\newpage
+
 # Surveys, sampling, and observational data {#sec-survey}
@@
 ## Similar Methodologies From Literature
-
-***Overview of Related Methods***
 
@@
 
-***Strengths of the Study***
+***Strengths & Limitations of the Study***
 
@@
 This suggests the method is generally consistent across age groups in terms of patterns of underestimation or overestimation.
-
-***Limitations of the Study***
 
@@
 These extra measurements aim to make predictions more accurate, especially for individuals at the lower or higher ends of the body fat range.
-
 Additionally, @potter highlighted that body fat is distributed differently between genders.
@@
 By concentrating on this group, the research aims to provide a method that better captures the specific fat distribution patterns and characteristics of this demographic.
-
-***Implications for Practical Applications***
 

### 2024-12-03 scripts/05-exploratory_data_analysis.R

@@ -44,5 +44,12 @@ while (length(final_variables) > 4) {
   final_variables <- setdiff(final_variables, names(which.min(aic_values)))
 }
 
+# Final 4-variable model
+final_model <- lm(as.formula(paste("Pct.BF ~", paste(final_variables,
+                                                     collapse = "+"))),
+                  data = data)
+
+summary(final_model)
+
 # Print the AIC value and final variables
 kable(final_variables)

### 2024-12-03 scripts/06-model_data.R

@@ -20,4 +20,4 @@ final_model <- lm(as.formula(paste("Pct.BF ~", paste(final_variables,
 summary(final_model)
 
 #### Save model ####
-saveRDS(final_model, file = "other/model/final_model.rds")
+saveRDS(final_model, file = "model/final_model.rds")

### 2024-12-03 scripts/06-model_data.R
folder name changes

@@ -20,4 +20,4 @@ final_model <- lm(as.formula(paste("Pct.BF ~", paste(final_variables,
 summary(final_model)
 
 #### Save model ####
-saveRDS(final_model, file = "model/final_model.rds")
+saveRDS(final_model, file = "models/final_model.rds")

### 2024-12-03 scripts/00-simulate_data.R
lintr fixes

@@ -56,7 +56,7 @@ repeat {
     Forearm = rnorm(n, mean = 27, sd = 3),
     Wrist = rnorm(n, mean = 18, sd = 2)
   )
-  
+
   if (all(simulated_data > 0)) {
     break
   }

### 2024-12-03 scripts/03-clean_data.R

@@ -33,7 +33,7 @@ remove_outliers <- function(data, column) {
   lower_bound <- max(q1 - 1.5 * iqr, epsilon)
   message(paste(column, ":", lower_bound))
   upper_bound <- q3 + 1.5 * iqr
-  
+
   data %>% filter(data[[column]] >= lower_bound & data[[column]] <= upper_bound)
 }
 

### 2024-12-03 scripts/05-exploratory_data_analysis.R

@@ -30,7 +30,7 @@ while (length(final_variables) > 4) {
                                                          collapse = "+"))),
                       data = data)
   current_aic <- AIC(current_model)
-  
+
   # Drop one variable at a time and calculate AIC
   aic_values <- sapply(final_variables, function(var) {
     temp_model <- lm(as.formula(paste("Pct.BF ~", paste(setdiff(final_variables,
@@ -39,7 +39,7 @@ while (length(final_variables) > 4) {
                      data = data)
     return(AIC(temp_model))
   })
-  
+
   # Remove the variable leading to the lowest AIC improvement
   final_variables <- setdiff(final_variables, names(which.min(aic_values)))
 }

### 2024-12-03 other/datasheet/datadictionary.qmd
graph label changes & title fixes

@@
 ---
-title: "Data Dictionary for Body Fat Raw Dataset"
+title: "Data Dictionary for Body Fat Percentage Raw Dataset"
 author: 

### 2024-12-03 other/datasheet/datasheet.qmd
graph label changes & title fixes

@@
 ---
-title: "Datasheet for Body Fat Dataset"
+title: "Datasheet for Body Fat Percentage Dataset"
 subtitle: "Predictive Modeling of Body Fat Percentage Using Body Measurements"

### 2024-12-03 paper/paper.qmd
graph label changes & title fixes

@@
 ---
-title: "Estimating Body Fat Percentage Using Anthropometric Measurements"
-subtitle: "Abdomen as the Strongest Predictor With Contributions From Wrist, Height, and Age For Affordable Health Monitoring"
+title: "Estimating Body Fat Percentage Using Anthropometric Measurements For Affordable Health Monitoring"
+subtitle: "Abdomen as the Strongest Predictor, Wrist & Height as Moderate Predictors, and Age as the Weakest Predictor"
 author: 
@@
 [@tbl-cleaned1] & [@tbl-cleaned2] & [@tbl-cleaned3] show the first 8 observations of the cleaned data.
+The cleaned data is used for the rest of the analysis in this paper.
 Additional cleaning steps included removing duplicates, addressing outliers, and removing missing observations to improve dataset’s usability.
@@
 hist(data$Pct.BF, 
-     main = "Histogram of Percent Body Fat",
-     xlab = "Percent Body Fat",
+     main = "Histogram of Body Fat Percentage",
+     xlab = "Body Fat Percentage",
+     ylab = "Frequency",
      col = "#f88379",
@@
 # Print the AIC value and final variables
-kable(final_variables)
+final_variables_table <- data.frame("Selected Variables" = final_variables)
+kable(final_variables_table)
 ```
@@
 # Histogram for each variable
-hist(data$Age, main = "Histogram of Age", xlab = "Age", col = "#7dbeff", border = "black")
-hist(data$Height, main = "Histogram of Height", xlab = "Height (cm)", col = "#2aebaa", border = "black")
-hist(data$Abdomen, main = "Histogram of Abdomen", xlab = "Abdomen (cm)", col = "#eb49a4", border = "black")
-hist(data$Wrist, main = "Histogram of Wrist", xlab = "Wrist (cm)", col = "#bb86f7", border = "black")
+hist(data$Age, main = "Histogram of Age", xlab = "Age", ylab = "Frequency", col = "#7dbeff", border = "black")
+hist(data$Height, main = "Histogram of Height", xlab = "Height (cm)", ylab = "Frequency", col = "#2aebaa", border = "black")
+hist(data$Abdomen, main = "Histogram of Abdomen", xlab = "Abdomen (cm)", ylab = "Frequency", col = "#eb49a4", border = "black")
+hist(data$Wrist, main = "Histogram of Wrist", xlab = "Wrist (cm)", ylab = "Frequency", col = "#bb86f7", border = "black")
 ```
@@
                          upper = list(continuous = wrap("points", color = "#008080", alpha = 0.4)),
-                         diag = list(continuous = wrap("densityDiag", fill = "#008080", alpha = 0.6)))
+                         diag = list(continuous = wrap("densityDiag", fill = "#008080", alpha = 0.6))) +
+  ggtitle("Relationship Between Selected Predictor Variables") +
+  theme(plot.title = element_text(hjust = 0.5))
 
@@
 
-# Print VIF values
-kable(vif_values)
+# Convert VIF values to a data frame
+vif_table <- data.frame("Predictor Variables" = names(vif_values), 
+                        "VIF Values" = as.numeric(vif_values))
+
+# Print the updated VIF table
+kable(vif_table)
 ```
@@
 plot(model$fitted.values, residuals(model), 
-     main = "Residuals vs Fitted",
-     xlab = "Fitted Values",
+     main = "Residuals vs Fitted Plot",
+     xlab = "Fitted Values of Model",
      ylab = "Residuals")
@@
 #| label: fig-variance
-#| fig-cap: Scale Location Verifying Constance Variance Assumption
+#| fig-cap: Scale Location Plot Verifying Constance Variance Assumption
 #| echo: false
@@
 
-plot(model, which = 3)
+plot(model, which = 3, sub = "")
 ```
@@
 
-# 4. Normality: Q-Q Plot of Residuals
-qqnorm(residuals(model))
+qqnorm(residuals(model), 
+       main = "Q-Q Plot of Residuals", 
+       xlab = "Theoretical Quantiles", 
+       ylab = "Sample Quantiles")
 qqline(residuals(model), col = "red")
@@
 #| fig-cap: Simple Linear Regression Plots Against Body Fat Percent for Age, Height, Abdomen, Wrist
+#| fig-height: 3.5
+#| fig-width: 6.2
 #| echo: false
@@
   geom_smooth(method = "lm", color = "red", se = FALSE) +
-  labs(title = "Pct.BF vs Age", x = "Age", y = "Pct.BF") +
+  labs(title = "Age vs Body Fat Percentage", x = "Age (years)", y = "Pct.BF (g/cm^3)") +
   theme_minimal()
@@
   geom_smooth(method = "lm", color = "red", se = FALSE) +
-  labs(title = "Pct.BF vs Height", x = "Height (inches)", y = "Pct.BF") +
+  labs(title = "Height vs Body Fat Percentage", x = "Height (cm)", y = "Pct.BF (g/cm^3)") +
   theme_minimal()
@@
   geom_smooth(method = "lm", color = "red", se = FALSE) +
-  labs(title = "Pct.BF vs Abdomen", x = "Abdomen (cm)", y = "Pct.BF") +
+  labs(title = "Abdomen vs Body Fat Percentage", x = "Abdomen (cm)", y = "Pct.BF (g/cm^3)") +
   theme_minimal()
@@
   geom_smooth(method = "lm", color = "red", se = FALSE) +
-  labs(title = "Pct.BF vs Wrist", x = "Wrist (cm)", y = "Pct.BF") +
+  labs(title = "Wrist vs Body Fat Percentage", x = "Wrist (cm)", y = "Pct.BF (g/cm^3)") +
   theme_minimal()
@@
   labs(
-    title = "Model Coefficients",
+    title = "Body Fat Percentage Model Coefficients",
     subtitle = "90% Confidence Intervals",
@@
 # Split into two smaller tables
-part1 <- raw_data[, 1:8]  # First 8 columns
-part2 <- raw_data[, 9:16]  # Remaining 8 columns
+raw_part1 <- raw_data[-1, 1:8]
+
+# Update column names to include units
+colnames(raw_part1) <- c(
+  "Density", "Pct.BF", "Age", "Weight", "Height", "Neck", "Chest", "Abdomen")
 
 # Render each part
-kable(head(part1, 10), booktabs = TRUE) %>%
+kable(head(raw_part1, 10), row.names = FALSE, booktabs = TRUE) %>%
   kable_styling(latex_options = c("hold_position", "scale_down"))
@@
 
-kable(head(part2, 10), booktabs = TRUE) %>%
+raw_part2 <- raw_data[-1, 9:16]
+
+colnames(raw_part2) <- c(
+  "Waist", "Hip", "Thigh", "Knee", "Ankle", "Bicep", "Forearm", "Wrist")
+
+kable(head(raw_part2, 10), row.names = FALSE, booktabs = TRUE) %>%
   kable_styling(latex_options = c("hold_position", "scale_down"))
@@
 #| label: fig-fullresidual
-#| fig-cap: Residual Plot Verifying the Linearity for All Variables
+#| fig-cap: Residual Plot Verifying the Linearity for Full Model
 #| echo: false
@@
 plot(fullresidual$fitted.values, residuals(fullresidual), 
-     main = "Residuals vs Fitted",
-     xlab = "Fitted Values",
+     main = "Residuals vs Fitted Plot",
+     xlab = "Fitted Values of Full Model",
      ylab = "Residuals")
@@
 #| label: fig-fullvariance
-#| fig-cap: Scale Location Verifying Constance Variance for All Variables
+#| fig-cap: Scale Location Plot Verifying Constance Variance for Full Model
 #| echo: false
@@
 
-plot(fullresidual, which = 3)
+plot(fullresidual, which = 3, sub = "", ann = FALSE)
+title(xlab = "Fitted Values of Full Model", 
+      ylab = "sqrt(|Standardized Residuals|)")
 ```
@@
 #| label: fig-fullnormality
-#| fig-cap: QQ-Plot Verifying the Normality of Errors for All Variables
+#| fig-cap: QQ-Plot Verifying the Normality of Errors for Full Model
 #| echo: false
@@
 # Normality: Q-Q Plot of Residuals
-qqnorm(residuals(fullresidual))
+qqnorm(residuals(fullresidual),
+       main = "Q-Q Plot of Residuals for Full Model", 
+       xlab = "Theoretical Quantiles of Full Model", 
+       ylab = "Sample Quantiles of Full Model")
 qqline(residuals(fullresidual), col = "red")

### 2024-12-03 scripts/03-clean_data.R
preamble corrections

@@ -3,6 +3,8 @@
 # Author: Wendy Yuan
 # Date: 29 November 2024
 # Contact: w.yuan@mail.utoronto.ca
+# Pre-requisites:
+# - 02-download_data.R must have been run
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-12-03 scripts/04-test_analysis_data.R

@@ -4,7 +4,7 @@
 # Date: 29 November 2024
 # Contact: w.yuan@mail.utoronto.ca
 # Pre-requisites:
-# - 02-clean_data.R must have been run
+# - 03-clean_data.R must have been run
 
 #### Workspace setup ####
 library(tidyverse)
